### 2018-10-28 manuscript/manuscript.tex
Started writing manuscript

\documentclass[preprint, a4paper, 10pt, times]{elsarticle}

\usepackage{lineno, hyperref}

\modulolinenumbers[5]

\journal{Agricultural and Forest Meteorology\tnoteref{mytitlenote}}

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
%\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frontmatter}

\title{A Multi-Satellite Investigation of the US Corn Belt in the Period 2010-2016 with a Focus on Solar-Induced Fluorescence}

%% Group authors per affiliation:
\author[uol,nceo]{Peter Somkuti\corref{cor1}\fnref{fn1}}
\ead{ps345@le.ac.uk}
\cortext[cor1]{Corresponding author, now at Colorado State University}
\fntext[fn1]{This is the specimen author footnote.}
\address[uol]{University of Leicester, Department of Physics of Astronomy, Leicester, UK}
\address[nceo]{National Centre for Earth Observation, University of Leicester, Leicester, UK}

\begin{abstract}
This template helps you to create a properly formatted \LaTeX\ manuscript.
\end{abstract}

\end{frontmatter}
\linenumbers

\section{Introduction}

Talk about corn belt, SIF, and other studies as well as their shortcomings. Mention especially the baseline problem.

\section{Materials \& Methods}
\subsection{Solar-Induced Fluorescence from GOSAT}

The Greenhouse Gases Observing Satellite (GOSAT) is the first mission solely dedicated to measure atmospheric concentrations of carbon dioxide (CO$_2$) and method (CH$_4$). Launched in early 2009 and operated by the Japan Aerospace Exploration Agency (JAXA), GOSAT employs a Fourier-transform spectrometer (TANSO-FTS) to passively measure sunlight back-reflected from the surface of the Earth. These hyper-spectral measurements are then used together with appropriate physical models and inversion schemes to retrieve the atmospheric concentration of trace gases like CO$_2$, CH$_4$ and even H$_2$O.

Due to the high spectral resolution of TANSO-FTS in the O$_2$ A-band at wavelength of $760\:\mathrm{nm}$, several solar (Fraunhofer) lines can be resolved and utilised for the retrieval of SIF. We utilise the retrieval method described in \citet{Frankenberg2011}. This so-called \textit{physically-based} retrieval is based on the Fraunhofer line discrimination method, first described in [REF]. Briefly summarised, the method relies on the fact that any additive radiation originating from the surface will reduce the fractional depth of Fraunhofer lines in the top-of-atmosphere (TOA) spectrum. It is therefore possible to decouple reflectance from the additive fluorescence contribution to the total TOA radiance. TANSO-FTS records radiances in the shortwave infrared wavelength range in two linear polarization states: P - parallel, and S - perpendicular to the plane of incidence (? or is it principal plane?).

To perform the GOSAT SIF retrievals we employ the University of Leicester Full-Physics algorithm \citep{Cogan2012}, called UoL-FP. It derives atmospheric and surface quantities from hyper-spectral measurements via its two components: a full-physics forward model, which accurately models the solar radiation entering and propagating through Earth's atmosphere, its interaction with the surface and finally the finite response at the detector on the space-based platform. The forward model calculations are then coupled with the second component of the algorithm: an inversion scheme that applies the Levenberg-Marquardt modification to the classic Gauss-Newton method, in order to modify the input parameters of the forward model (the so-called state vector) to match model calculation with real measurements. Inferring atmospheric and surface quantities as well as quantifying the uncertainty on each retrieved parameter is performed using a Bayesian optimal estimation (OE) framework according to \citet{Rodgers2000}.

We make use of the same processing pipeline which was previously used for the generation of high-quality atmospheric trace gas data sets \citep{Buchwitz2017} at the University of Leicester, using the same core full-physics algorithm.

The surface pressure is informed by the ECMWF ERA-Interim model, whereas the surface albedo is estimated through the measured radiances themselves assuming a Lambertian surface model.

 GOSAT retrievals over land surfaces from January 2010 until December 2016 were processed using ECWMF ERA-Interim data for surface pressure and specific humidity profiles. , and both radiances were processed independently. To remove the scenes with significant cloud contamination, a cloud screening algorithm was run beforehand.

\subsection{Spatially and Temporally Collocated Satellite Measurements}
\subsection{Carbon Fluxes from Inversion of GOSAT CO2 Retrievals}
\subsection{Agricultural Statistics from USDA}

\section{Results}

\begin{figure}[htbp]
\centering
\includegraphics{../SIF_overview.pdf}
\caption{default}
\label{default}
\end{figure}

\section*{References}
\bibliography{mybibfile}

\end{document}

### 2018-10-28 analysis.py

@@ -1,15 +1,27 @@
+from matplotlib import rcParams
+rcParams['font.family'] = 'serif'
+rcParams['font.serif'] = ['Times', 'Times New Roman']
+
+rcParams['xtick.labelsize'] = 7
+rcParams['ytick.labelsize'] = 7
+rcParams['ytick.labelsize'] = 7
+rcParams['axes.labelsize'] = 8
+rcParams['mathtext.fontset'] = 'stix'
+
+from matplotlib import pyplot as plt
+
 import h5py
 import numpy as np
 import pandas as pd
-from netCDF4 import num2date
+from netCDF4 import num2date, Dataset
 
-from matplotlib import rcParams
-rcParams['font.family'] = 'serif'
-rcParams['font.sans-serif'] = ['Times New Roman']
+from scipy.interpolate import RegularGridInterpolator as RGI
+import itertools
 
-from matplotlib import pyplot as plt
 import palettable as pt
 import statsmodels.formula.api as smf
+
+from bbox import *
 
 ###############################################################################
 ## Change analysis parameters here
@@ -17,15 +29,15 @@ import statsmodels.formula.api as smf
 
 resample = 'MS'
 rs_apply = 'mean'
-min_count = 50
+min_sif = 0.0
+min_count = 200
 min_date = '20100101'
 max_date = '20161231'
 anomaly_stat = 'median'
 
 ###############################################################################
+######### PREPPING DATA #######################################################
 
-
-######### PREPPING DATA ###########
 
 ### Read in the USDA data
 
@@ -49,52 +61,96 @@ usda_production = pd.read_csv('corn_soy_wheat_production.csv', sep=',', thousand
 h5 = h5py.File('fluorescence_subset.h5', 'r')
 dates = num2date(h5['frac_days_since'][:], units='days since 1970-01-01')
 
-qual = (h5['qual_flag'][:] == 1)
-
 # Create dataframe using the dates, and then read all 1-dim data arrays into it
-df = pd.DataFrame(index=dates[qual])
+df = pd.DataFrame(index=dates)
 
+print("Reading HDF")
 for key in h5.keys():
     if len(h5[key].shape) == 1:
         if h5[key].shape[0] == len(h5['Exposure_id']):
             # Don't want the empty 'simple' fields
[…]

### 2018-10-28 subset_fluorescence.py

@@ -16,14 +16,22 @@ h5_P = h5py.File('/Users/petersomkuti/Work/fluorescence/fluor_concatenated_P.h5'
 
 intersect = np.intersect1d(h5_S['Exposure_id'][:],
                            h5_P['Exposure_id'][:])
+union = np.union1d(h5_S['Exposure_id'][:],
+                   h5_P['Exposure_id'][:])
 
 print("{:d} common soundings.".format(len(intersect)))
+print("{:d} union soundings.".format(len(union)))
 
-srt_S = np.searchsorted(h5_S['Exposure_id'][:], intersect)
-srt_P = np.searchsorted(h5_P['Exposure_id'][:], intersect)
+srt_S = np.searchsorted(union, h5_S['Exposure_id'][:])
+srt_P = np.searchsorted(union, h5_P['Exposure_id'][:])
 
-lon = h5_S['lon'][:][srt_S]
-lat = h5_S['lat'][:][srt_S]
+lon = np.zeros(len(union))
+lat = np.zeros(len(union))
+
+lon[srt_S] = h5_S['lon'][:]
+lat[srt_S] = h5_S['lat'][:]
+lon[srt_P] = h5_P['lon'][:]
+lat[srt_P] = h5_P['lat'][:]
 
 subset_idx = np.where((lon >= lon_min) & (lon <= lon_max) &
                       (lat >= lat_min) & (lat <= lat_max))[0]
@@ -34,8 +42,6 @@ skip_list = ['a_CO2', 'a_CH4', 'a_O2', 'a_H2O', 'a_aero1', 'a_aero1_tot',
              'a_ic', 'a_ic_tot', 'a_strat', 'a_strat_tot',
              'r_akfull_755', 'r_akfull_772',
              'r_pwgts_755', 'r_pwgts_772']
-
-subset_list_S = srt_S[subset_idx].tolist()
 
 with h5py.File('fluorescence_subset.h5', 'w') as h5_out:
 
@@ -49,16 +55,43 @@ with h5py.File('fluorescence_subset.h5', 'w') as h5_out:
         
         print(key)
         if (h5_S[key].shape[0] == len(h5_S['Exposure_id'])):
+            
+            if ('corr' in key) or (key[:2] == 'r_') or (key == 'qual_flag'):                
+                this_key_S = key + '_S'
+                this_key_P = key + '_P'
+                this_data_S = np.zeros(len(union), dtype=h5_S[key].dtype)
[…]

### 2018-11-03 manuscript/manuscript.tex
Did some work on the manuscript and plots again.

@@
 \subsection{Solar-Induced Fluorescence from GOSAT}
+\label{sec:GOSAT_SIF}
 
@@
 We utilise the retrieval method described in \citet{Frankenberg2011}.
-This so-called \textit{physically-based} retrieval is based on the Fraunhofer line discrimination method, first described in [REF].
+This so-called \textit{physically-based} retrieval is derived from the Fraunhofer line discrimination method, first described in [REF].
 Briefly summarised, the method relies on the fact that any additive radiation originating from the surface will reduce the fractional depth of Fraunhofer lines in the top-of-atmosphere (TOA) spectrum.
@@
 It derives atmospheric and surface quantities from hyper-spectral measurements via its two components: a full-physics forward model, which accurately models the solar radiation entering and propagating through Earth's atmosphere, its interaction with the surface and finally the finite response at the detector on the space-based platform.
-The forward model calculations are then coupled with the second component of the algorithm: an inversion scheme that applies the Levenberg-Marquardt modification to the classic Gauss-Newton method, in order to modify the input parameters of the forward model (the so-called state vector) to match model calculation with real measurements.
+The forward model calculations are then coupled with the second component of the algorithm: a non-linear inversion scheme that applies the Levenberg-Marquardt modification to the Gauss-Newton method, in order to modify the input parameters of the forward model (the so-called state vector) to match model calculation with real measurements.
 Inferring atmospheric and surface quantities as well as quantifying the uncertainty on each retrieved parameter is performed using a Bayesian optimal estimation (OE) framework according to \citet{Rodgers2000}.
 
-We make use of the same processing pipeline which was previously used for the generation of high-quality atmospheric trace gas data sets \citep{Buchwitz2017} at the University of Leicester, using the same core full-physics algorithm.
+We make use of the same processing pipeline which was previously utilized for the generation of high-quality atmospheric trace gas data sets \citep{Buchwitz2017,Trent2018} at the University of Leicester, using the same core retrieval algorithm.
+On a per-scene (measurement) basis, the surface pressure is informed by the ECMWF ERA-Interim model, and the surface albedo is estimated through the measured radiances themselves assuming a Lambertian surface model.
 
-The surface pressure is informed by the ECMWF ERA-Interim model, whereas the surface albedo is estimated through the measured radiances themselves assuming a Lambertian surface model.
+Following the retrieval strategy in \citet{Frankenberg2011}, we retrieve SIF at two micro-windows at $755\:\mathrm{nm}$ ($755.86 - 758.95$ nm) and $772\:\mathrm{nm}$ ($769.59 - 774.83$ nm), as well as the two polarizations, independently.
+For both retrieval windows, the SIF radiances are represented by a constant additive offset to the TOA radiances, along with a linear surface albedo (constant + slope), and instrument dispersion shift and stretch.
+As there are weak oxygen lines present in the $772\:\mathrm{nm}$ window, surface pressure is additionally retrieved in that micro-window.
+To exclude any scenes with large cloud contamination, we ran a cloud-screening algorithm beforehand.
+Only those GOSAT scenes are processed where the apparent surface pressure deviated by less than $100\:\mathrm{hPa}$ from the ERA-Interim prediction.
 
- GOSAT retrievals over land surfaces from January 2010 until December 2016 were processed using ECWMF ERA-Interim data for surface pressure and specific humidity profiles.
-, and both radiances were processed independently.
-To remove the scenes with significant cloud contamination, a cloud screening algorithm was run beforehand.
+A crucial step in the SIF retrieval process is the bias correction.
+As established by \citet{Frankenberg2011}, small non-linearities in the analogue-to-digital conversion of the TANSO-FTS interferograms lead to the same fractional reduction of Fraunhofer lines as any SIF signal would do and thus result in unphysical SIF values.
+In order to rid the measurements of these instrument artefacts, the retrieved SIF values need to be corrected.
+To achieve the bias correction, we apply a slightly different method compared to \citet{Frankenberg2011}.
+First, we use the ESA CCI Land Cover map v2.0.7 \citep{Bontemps2013} to obtain the land cover classes for the surfaces seen by each GOSAT measurement (see Section~\ref{sec:collocation}).
+To identify footprints which can be assumed to be permanently free of vegetation, we consider only surfaces where at least $95\%$ of all land cover-class pixels within the footprint belong to the types: urban, desert, snow and ice, or any bare type.
+This approach has the advantage that not only highly reflective surfaces like ice shields or deserts are used for the correction process, but also darker surfaces such as mountainous regions.
 
-\subsection{Spatially and Temporally Collocated Satellite Measurements}
+The calibration curve is produced via the relationship between retrieved offset ($z_0$) and the mean radiance in the entire first GOSAT band ($\overline{I}_1$).
+Ideally, this curve would be flat, centered around zero, however the instrumental artefacts lead to a somewhat complicated shape, as shown in Figure XX [should I put a figure here?
+or is this too technical already..].
+As this bias is of purely instrumental nature, it is not necessarily safe to assume that the bias remained the same over the long operational time of the instrument.
+Thus, we adopt three different strategies to correct for this instrumental bias.
+For the first one, we collect retrievals over non-fluorescing areas in seasonal aggregates (DJF, MAM, JJA, SON).
+For every season in every year the SIF retrievals are being corrected according to the calibration curve derived at that particular season-year combination.
+The second strategy is similar, the only difference being that retrievals for an entire year are collected.
+The main difference in the two methods is the aggregation period: shorter periods make the calibration curves noisy, however are more able to catch instrumental issues which may affect the bias.
+The third and most elaborate strategy takes the time-dependence more explicitly into account.
+First, the all retrievals over non-fluorescing areas are collected and binned two dimensionally: monthly bins for the time dimension, and $14$ bins in the radiance dimension.
+Through this regular 2D grid, a spline interpolation function is used to calculate the bias at any given point in time-radiance space.
+
+\subsection{Spatially and Temporally Collocated Earth Observation Data}
+\label{sec:collocation}
+
+GOSAT/TANSO-FTS was designed to measure atmospheric quantities, and thus differs from imaging-type measurement concepts (e.g.~MODIS) that are tailored to the measurement of surface quantities.
+The high-resolution spectrometer points at one location at a time with an instantaneous field of view (IFOV) of ZYX$^\circ$, which corresponds roughly to a circular footprint with $10.5\:\mathrm{km}$ diameter at nadir viewing geometry.
+As a consequence, it is necessary to consider the specific sampling pattern for the data sets in the analysis in order to avoid sampling bias (see Section~\ref{sec:sampling_bias}).
+
+For every GOSAT scene, we consider the full footprint as defined by the four extremal points of the footprint ellipse (as given in the L1B data).
+The following Earth observation datasets are then sampled:
+
+\begin{itemize}
+\item ESA CCI Land Cover v2.0.7 ($300\:\mathrm{m}$ resolution, $2010-2015$, for scenes after $2015$, the $2015$ map was used) \citep{Bontemps2013}
+\item ESA CCI Soil Moisture v3.2 ($0.25^\circ$ resolution, $2010-2015$) \citep{Dorigo2017}
+\item MODIS/Aqua MYD13C1 V006 Vegetation Indices ($0.05^\circ$ resolution, $2010-2016$) \citep{MYD13C1}
+\item MODIS/Aqua MYD11C2 V006 Land Surface Temeprature ($0.05^\circ$ resolution, $2010-2016$) \citep{MYD11C2}
+\item SPOT/VEGETATION Leaf Area Index V2.0.1 ($1\:\mathrm{km}$ resolution, $2010-2016$)
+\item SPOT/VEGETATION Fractional Vegetation Cover V2.0.1 ($1\:\mathrm{km}$ resolution, $2009-2016$)
+\item TRMM (3B43, multi-satellite) precipitation ($0.25^\circ$ resolution, $2010-2016$)
+\end{itemize}
+
+For the MODIS/Aqua, ESA CCI Land Cover and SPOT/VEGETATION datasets, the scene-specific footprint is fully taken into account.
+Only those pixels are aggregated to the scene-specific value, whose pixel area overlaps by at least $50\%$ with the GOSAT footprint.
+Soil moisture and TRMM precipitation data, however, are of lower resolution where sub-pixel aggregation is not required.
+For TRMM, the grid box is taken in which the GOSAT footprint lies, and for the soil moisture data (which is supplied on grid points rather than grid boxes [DOUBLE CHECK!!]), bi-linear interpolation of the closest four grid points is used.
+
+In the time dimension, linear interpolation is used for all data sets except for land cover data (annual) and TRMM (monthly).
+
 \subsection{Carbon Fluxes from Inversion of GOSAT CO2 Retrievals}
+\label{sec:fluxes}
+LIANG PLEASE HELP!
+
 \subsection{Agricultural Statistics from USDA}
+\label{sec:usda}
+
+\subsection{GOSAT Sampling Bias}
+\label{sec:sampling_bias}
+
+As mentioned during the discussion on GOSAT SIF retrievals (Section~\ref{sec:GOSAT_SIF}), the FTS instrument, due to its pointing strategy/nature, causes potential sampling biases due to the pointing locations.
+While there is an inherent bias due to clouds, as GOSAT SIF retrievals can not be performed in the presence of thick clouds, the sampling strategy results in non-uniform selection of surfaces throughout the region of interest.
+Illustrated in Figure~\ref{fig:sampling}, the sampling density is shown for the entire time period from the beginning of $2010$ until the end of $2016$.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{../coverage_map.png}
+\caption{Land cover classes (left) and GOSAT sampling density shown for the region of interest ($104$W - $87.5W$, $37$N - $49$N).
+Yellow land cover pixels correspond to crop, orange represents grassland, green-colored pixels are various tree types, and red areas are urban regions.
+In the right picture, all GOSAT soundings for the entire time period $2010-2016$ are collected and visualized as a density map to illustrate the both sparse and irregular sampling pattern.}
+\label{fig:sampling}
+\end{figure}
+
+The question arises, whether the sampling of the various surfaces of the chosen region of interest is representative of the entire area.
+To that end, we compare the most common land cover classes (Figure~\ref{fig:sampling} left) of the entire region of interest at the native resolution ($300\:\mathrm{m}$) of the ESA CCI Land Cover data set (excluding water bodies) to the sub-pixel aggregated data at the location of the GOSAT footprints.
+The result of the relative occurrence of the six most common types is shown in Figure~\ref{fig:lc_coverage}.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{../lc_coverage.pdf}
+\caption{default}
+\label{fig:lc_coverage}
+\end{figure}
+
+Not surprising, more than $75\%$ of surfaces belong to either rainfed cropland or grassland types.
+The third most common surface type (deciduous tree cover) is mainly due to Ozark National Forest in Missouri, Superior National Forest as well as forests in northern Wisconsin.
+For the total period, GOSAT is well representing the overall composition of land cover classes of the region of interest.
+The largest differences are seen for flooded tree cover, where GOSAT is slightly over-repensenting ($+1.69\%$), and grassland, where GOSAT is under-representing ($-3.25\%$).
+
+Repeating the same analysis on a monthly basis, a different picture than Figure~\ref{fig:lc_coverage} can arise, as GOSAT's sampling is not only non-uniform geographically, but also changed over time.
+In Figure~\ref{fig:lc_diff_monthly}, the differences between GOSAT-seen and total ROI land cover class coverage for monthly aggregates is shown for the three most prevalent classes.
+We observe that differences can change somewhat drastically, and for certain months even reach $10\%$.
+The problematic months, in which the differences are fairly large for cropland and grassland LC types are $2013/04$, $2014/02$, $2014/03$, $2014/04$, $2014/11$, $2016/08$, $2015/02$ and $2015/04$.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{../lc_diff_monthly.pdf}
+\caption{Jan 2015 has not been taken into account due to the low number of measurements in that month.}
+\label{fig:lc_diff_monthly}
+\end{figure}
 
@@
 \caption{default}
-\label{default}
+\label{fig:sif_ts}
 \end{figure}
 
-\section*{References}
+\section*{}
 \bibliography{mybibfile}

### 2018-11-03 analysis.py

@@ -1,3 +1,4 @@
+import matplotlib
 from matplotlib import rcParams
 rcParams['font.family'] = 'serif'
 rcParams['font.serif'] = ['Times', 'Times New Roman']

### 2018-11-03 sampling_bias.py

@@ -1,3 +1,22 @@
+#import matplotlib
+#matplotlib.use('agg')
+
+from matplotlib import rcParams
+
+rcParams['font.family'] = 'serif'
+rcParams['font.serif'] = ['Times', 'Times New Roman']
+
+rcParams['xtick.labelsize'] = 7
+rcParams['ytick.labelsize'] = 7
+rcParams['ytick.labelsize'] = 7
+rcParams['axes.labelsize'] = 8
+rcParams['axes.titlesize'] = 10
+rcParams['mathtext.fontset'] = 'stix'
+
+
+
+
+
 import h5py
 from netCDF4 import Dataset
 import numpy as np
@@ -22,6 +41,8 @@ lc_labels[2] = "Rainfed cropland\n(herbaceous cover)"
 lc_labels[6] = "Mosaic natural vegetation\n(tree, shrub, herbaceous cover)\n(>50%) / cropland (<50%)"
 lc_labels[8] = "Tree cover, broadleaved,\ndeciduous (closed to open >15%)"
 lc_labels[28] = "Tree cover, flooded,\nfresh or brakish water"
+lc_labels[17] = "Tree cover, mixed leaf type\n(broadleaved and needleleaved)"
+
 
 # Read the fluorescence subset
 gosat_h5 = h5py.File('fluorescence_subset.h5', 'r')
@@ -69,27 +90,89 @@ lc_sort_GOSAT = np.argsort(lc_un_GOSAT[1])[::-1]
 
 # Make a nice barplot with the results
 bar_width = 0.25
-plt.figure(figsize=(4,3), dpi=300)
+plt.figure(figsize=(2.5, 3), dpi=300)
 
-plt.bar(np.arange(len(lc_percs_ALL)) - bar_width / 2,
-        lc_percs_ALL[lc_sort_ALL],
-        bar_width, label='Region of interest')
+plt.barh(np.arange(len(lc_percs_ALL)) - bar_width / 2,
+         lc_percs_ALL[lc_sort_ALL],
+         bar_width, label='Region of interest')
 
-plt.bar(np.arange(len(lc_percs_ALL)) + bar_width / 2,
-        lcsum[lc_sort_ALL],
-        bar_width, label='GOSAT sampling')
+plt.barh(np.arange(len(lc_percs_ALL)) + bar_width / 2,
+         lcsum[lc_sort_ALL],
+         bar_width, label='GOSAT sampling')
 
-plt.xticks(np.arange(len(lc_percs_ALL)),
[…]

### 2018-11-10 manuscript/manuscript.tex
Added to the manuscript..

@@
 As mentioned during the discussion on GOSAT SIF retrievals (Section~\ref{sec:GOSAT_SIF}), the FTS instrument, due to its pointing strategy/nature, causes potential sampling biases due to the pointing locations.
-While there is an inherent bias due to clouds, as GOSAT SIF retrievals can not be performed in the presence of thick clouds, the sampling strategy results in non-uniform selection of surfaces throughout the region of interest.
+While there is an inherent bias due to clouds, as GOSAT SIF retrievals can not be performed in the presence of thick clouds, the sampling strategy results in non-uniform selection of surfaces throughout the region of interest (ROI).
 Illustrated in Figure~\ref{fig:sampling}, the sampling density is shown for the entire time period from the beginning of $2010$ until the end of $2016$.
@@
 We observe that differences can change somewhat drastically, and for certain months even reach $10\%$.
-The problematic months, in which the differences are fairly large for cropland and grassland LC types are $2013/04$, $2014/02$, $2014/03$, $2014/04$, $2014/11$, $2016/08$, $2015/02$ and $2015/04$.
+Months in which the differences are fairly large for cropland and grassland LC types are: $2013/04$, $2014/02$, $2014/03$, $2014/04$, $2014/11$, $2015/02$ and $2015/04$, $2016/08$.
+Due to the careful handling of the EO data set sampling, the difference in LC coverage should not have a significant impact on the further analysis and results.
+It is also important to note that while Figures~\ref{fig:lc_coverage} and \ref{fig:lc_diff_monthly} confirm that the LC classes are more or less well-represented, vegetation responses can vary geographically over the corn belt, even though they might share the same LC classification.
 
@@
 
+\subsection{Time Series}
+
+The SIF retrievals are aggregated on a monthly basis, where the mean of all measurements inside the ROI for a given month are considered.
+As we have two different polarisations (P, S) and three different calibration procedures (seasonal, annual, spline-based), there are a total of six SIF time series.
+Figure~\ref{fig:sif_ts} shows this ensemble of SIF data, where the thick line is the median of all six time series, and the shaded area visualizes the minimum and maximum value of the given month to show the spread of the ROI-averaged SIF.
+It should be noted that the variability in the SIF time series stems mostly from the two different polarisations, rather than the calibration methodology.
+Months with less than $200$ measurements are dropped from both the visualization and the analysis, which affects only January $2015$, a month in which GOSAT was only partially operative due to instrumental issues.
+
 \begin{figure}[htbp]
@@
 
+The anomalies in Figure~\ref{fig:sif_ts} (bottom) are calculated as the difference between the current month and the median of all of the same months over the seven-year period.
+While the straight time series does not immediately reveal any striking features, the anomalies show several important ones.
+First, it is clear that over this relatively short period of seven years, the number of anomalous months within that period somewhat large: counting the number of months where the SIF signal exceeds the standard deviation of the all anomalies (dotted green lines in Fig.~\ref{fig:sif_ts}), one arrives at $22$ (or $26\%$) anomalous months.
+We conclude that this short time period does not have a strong baseline, as every year has at least two anomalous months.
+[REFERENCE WOLF LIU AND OTHERS AND POINT OUT THAT THEY USED A SIMPLE BASELINE] It is therefore imperative to look at every anomaly within the context of other climatological and agricultural drivers.
+
+In chronological order, the big anomalies can be easily identified and related to known meteorological events.
+Starting in 2010, we see the effects of the rapid El Ni\~no-La Ni\~na transition, which brought excessive rain to the corn belt in the summer months (Fig.~\ref{fig:anomalies_0} bottom row) and drove plant growth.
+
+In $2011$, we see a negative anomaly for spring, despite average precipitation and temperatures for that season.
+The reason for the negative anomaly is hinted at by the positive GRACE anomaly for $2011$ (Fig.~\ref{fig:anomalies_0} middle row).
+Large amounts of melting snow in the northern corn belt, as well as high precipitation in the south eastern corner (Missouri) have caused massive flooding of the Mississippi and Missouri rivers.
+As most parts of the ROI have not seen any increased rainfall, the anomaly plot in Figure~\ref{fig:anomalies_0} (bottom) does not show any significant outlier.
+The flooded areas, however, are visible as a positive anomaly in the GRACE data.
+The flooding has not only delayed planting progress, but also
+
+The two anomalies in $2012$ are the most well-known and most-studied ones.
+In short, a warm winter and warm spring (see LST anomalies in Fig.~\ref{fig:anomalies_2} top) caused early and fast vegetation growth.
+In the following summer, however, anomalously low precipitation (Fig.~\ref{fig:anomalies_0} bottom) was responsible for drought conditions.
+As a consequence of the early spring onset due to warm temperatures, the plants used up soil water reserves quicker and depleted the soil of moisture, thus exacerbating the drought even further.
+This $2012$ drought was one of the most severe droughts in recorded history, with conditions comparable to the $1930$'s dustbowl era.
+The drought conditions are seen equally strongly in the soil moisture (Fig.~\ref{fig:anomalies_2} middle and bottom) anomalies [WHY IS PASSIVE NOT AS NICE HERE?], as well as the GRACE anomalies (Fig.~\ref{fig:anomalies_0} middle).
+
+In $2013$ and $2014$, we again see a negative anomaly for spring and early summer. Despite the anomalies looking similar, they can be explained differently.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{../anomalies_755_abs_0_median.pdf}
+\caption{default}
+\label{fig:anomalies_0}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{../anomalies_755_abs_2_median.pdf}
+\caption{default}
+\label{fig:anomalies_2}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{../anomalies_755_abs_1_median.pdf}
+\caption{default}
+\label{fig:anomalies_1}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{../anomalies_755_abs_3_median.pdf}
+\caption{default}
+\label{fig:anomalies_3}
+\end{figure}
+
 \section*{}

### 2018-11-10 analysis.py

@@ -36,6 +36,9 @@ min_date = '20100101'
 max_date = '20161231'
 anomaly_stat = 'median'
 
+problem = ['2013-04-01', '2014-02-01', '2014-03-01', '2014-04-01',
+           '2014-11-01', '2015-02-01', '2015-04-01', '2016-08-01']
+
 ###############################################################################
 ######### PREPPING DATA #######################################################
 
@@ -274,7 +277,14 @@ def ts_overview(plot_df, sif_list, aux_list,
         
         ax.plot(plot_df.loc[:, aux],
                 #color=aux_colors[i],
-                label=aux_label)
+                label=aux_label, zorder=5)
+        '''
+        for p in problem:
+            pl = np.where(plot_df.index == p)[0][0]
+            ax.scatter(plot_df.index[pl],
+                       plot_df.iloc[pl].loc[aux],
+                       s=3, color='r', zorder=10)
+        '''               
         
         if symm_lim:
             ax.set_ylim(-aux_lim, aux_lim)
@@ -342,8 +352,14 @@ for pol in ['_P', '_S', '']:
                           y1=dfa.loc[:, SL[f'abs_755{pol}']].min(axis=1),
                           y2=dfa.loc[:, SL[f'abs_755{pol}']].max(axis=1),
                           color='green', alpha=0.15)
+
+    anomaly_std = dfa.loc[:, SL[f'abs_755{pol}']].median(axis=1).std()
+    
     axarr[1].hlines([0], xmin=dfa.index[0], xmax=dfa.index[-1],
-                    color='grey', linewidth=1.0, linestyle='dashed')
+                    color='grey', linewidth=0.5, linestyle='solid')
+    axarr[1].hlines([-anomaly_std, anomaly_std], xmin=dfa.index[0], xmax=dfa.index[-1],
+                    color='green', linewidth=0.5, linestyle='dotted')
+    
     axarr[1].set_ylabel('SIF Anomaly\n[mW/m$^2$/sr/nm]')
 
     fig.align_ylabels()
@@ -358,7 +374,7 @@ for pol in ['_P', '_S', '']:
     plt.close('all')
 
 aux_list = ['gome2_sif',
-            'spei',
+            'GRACE',
             'trmm_precip',
             #######
             'myd13_evi',
@@ -366,13 +382,13 @@ aux_list = ['gome2_sif',
             'lai',
             #######
             'myd11_lst_day',
[…]

### 2018-11-12 manuscript/manuscript.tex
More work

@@
-\documentclass[preprint, a4paper, 10pt, times]{elsarticle}
+\documentclass[review, a4paper, 10pt, times]{elsarticle}
 
@@
 \author[uol,nceo]{Peter Somkuti\corref{cor1}\fnref{fn1}}
-\ead{ps345@le.ac.uk}
+\ead{psomkuti@colostate.edu}
+\author[uol,nceo]{Hartmut B\"osch}
+\author[uoe,nceo]{Paul Palmer}
+\author[uoe,nceo]{Liang Feng}
+\author[uol,nceo]{Robert Parker}
+\author[nceo]{Tristan Quaife}
+
 \cortext[cor1]{Corresponding author, now at Colorado State University}
@@
 \address[nceo]{National Centre for Earth Observation, University of Leicester, Leicester, UK}
+\address[uoe]{University of Edinburgh, Edinburgh, UK}
 
@@
 
-Talk about corn belt, SIF, and other studies as well as their shortcomings. Mention especially the baseline problem.
+Talk about Corn Belt, SIF, and other studies as well as their shortcomings. Mention especially the baseline problem.
 
@@
 Due to the careful handling of the EO data set sampling, the difference in LC coverage should not have a significant impact on the further analysis and results.
-It is also important to note that while Figures~\ref{fig:lc_coverage} and \ref{fig:lc_diff_monthly} confirm that the LC classes are more or less well-represented, vegetation responses can vary geographically over the corn belt, even though they might share the same LC classification.
+It is also important to note that while Figures~\ref{fig:lc_coverage} and \ref{fig:lc_diff_monthly} confirm that the LC classes are more or less well-represented, vegetation responses can vary geographically over the Corn Belt, even though they might share the same LC classification.
 
@@
 \subsection{Time Series}
+\label{sec:SIF_TS}
 
@@
 While the straight time series does not immediately reveal any striking features, the anomalies show several important ones.
-First, it is clear that over this relatively short period of seven years, the number of anomalous months within that period somewhat large: counting the number of months where the SIF signal exceeds the standard deviation of the all anomalies (dotted green lines in Fig.~\ref{fig:sif_ts}), one arrives at $22$ (or $26\%$) anomalous months.
+First, it is clear that over this relatively short period of seven years, the number of anomalous months within that period somewhat large: counting the number of months where the SIF signal exceeds the standard deviation of all anomalies (dotted green lines in Fig.~\ref{fig:sif_ts}, ), one arrives at $22$ (or $26\%$) anomalous months.
 We conclude that this short time period does not have a strong baseline, as every year has at least two anomalous months.
-[REFERENCE WOLF LIU AND OTHERS AND POINT OUT THAT THEY USED A SIMPLE BASELINE] It is therefore imperative to look at every anomaly within the context of other climatological and agricultural drivers.
+[REFERENCE WOLF LIU AND OTHERS AND POINT OUT THAT THEY USED A SIMPLE BASELINE] It is therefore imperative to look at every anomaly within the context of other climatological and agricultural drivers.In chronological order, the big anomalies can be easily identified and related to known meteorological events.
 
-In chronological order, the big anomalies can be easily identified and related to known meteorological events.
-Starting in 2010, we see the effects of the rapid El Ni\~no-La Ni\~na transition, which brought excessive rain to the corn belt in the summer months (Fig.~\ref{fig:anomalies_0} bottom row) and drove plant growth.
+Starting in $2010$, we see the effects of the rapid El Ni\~no-La Ni\~na transition, which brought excessive rain to the Corn Belt in the summer months (Fig.~\ref{fig:anomalies_0} bottom row) and drove plant growth.
 
@@
 The reason for the negative anomaly is hinted at by the positive GRACE anomaly for $2011$ (Fig.~\ref{fig:anomalies_0} middle row).
-Large amounts of melting snow in the northern corn belt, as well as high precipitation in the south eastern corner (Missouri) have caused massive flooding of the Mississippi and Missouri rivers.
+Large amounts of melting snow in the northern Corn Belt, as well as high precipitation in the south eastern corner (Missouri) have caused massive flooding of the Mississippi and Missouri rivers.
 As most parts of the ROI have not seen any increased rainfall, the anomaly plot in Figure~\ref{fig:anomalies_0} (bottom) does not show any significant outlier.
 The flooded areas, however, are visible as a positive anomaly in the GRACE data.
-The flooding has not only delayed planting progress, but also
+The flooding has not only delayed planting progress, but also SOMETHING
 
@@
 
-In $2013$ and $2014$, we again see a negative anomaly for spring and early summer. Despite the anomalies looking similar, they can be explained differently.
+In $2013$ and $2014$, we again see a negative anomaly for spring and early summer.
+For these two years, the anomalies have similar causes.
+In the spring months, high precipitation and cool temperatures delayed the planting process - corn seed planting is generally done on warm and dry days - as well as caused slow maturing of crops.
+[POINT TO USDA GRAPHS].
+
+The following two years exhibit positive SIF anomalies.
+In $2015$, near-ideal temperatures and favourable rainfall have led to good growing an maturing conditions for corn and soybeans, despite the rainfall distribution being suboptimal - the southern and eastern regions of the Corn Belt experienced more excessive rain.
+$2016$ proved to be an even better year for crop production than $2015$, and this is reflected in the SIF anomaly.
+After an intense El Ni\~no in $2015$, the quick transition to a weak La Ni\~na, and a fairly wet summer has provided ideal conditions for crops.
 
@@
 
+\section{Crop planting and yield}
+
+The US Corn Belt is a very specific type of biome.
+As recently investigated by \citet{Alter2017}, it even generates its own climate.
+Despite the ROI being almost $1800 \cdot 10^9\;\mathrm{m}^2$ ($\approx 440$ million acres) in area, almost half of it is managed cropland.
+Meteorological conditions are thus not the only factor in determining the onset and productivity of one given season.
+It was pointed out in Section~\ref{sec:SIF_TS} that certain for years, the rainfall amount in springtime have caused delays in the planting of crops.
+To show that SIF indeed captures the delays in planting, we compare against the USDA crop progress reports.
+In these reports, the percentage of acreage planted is recorded based on farmer surveys.
+We translate these state-wide and weekly data for the whole ROI by multiplying with the total planted area for that given year and state in order to obtain an effective "planted area".
+We compare this number for every year against the integrated SIF radiances from Feburary onwards to June.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{../corn_soy_planted_sif.pdf}
+\caption{default}
+\label{fig:corn_soy_planted_sif}
+\end{figure}
+
+The result for both corn and soybeans is shown in Figure~\ref{fig:corn_soy_planted_sif}.
+It shows that the time-integrated SIF radiances correspond very well to the crop planting progress of that given year at the first week of May (week 18).
+[TODO: If I change the months / weeks slightly - the result improves a bit; justification?]
+
 \section*{}

### 2018-11-12 analysis.py

@@ -16,6 +16,8 @@ import numpy as np
 import pandas as pd
 from netCDF4 import num2date, Dataset
 
+import scipy as sp
+from scipy import stats as sps
 from scipy.interpolate import RegularGridInterpolator as RGI
 import itertools
 
@@ -40,6 +42,15 @@ problem = ['2013-04-01', '2014-02-01', '2014-03-01', '2014-04-01',
            '2014-11-01', '2015-02-01', '2015-04-01', '2016-08-01']
 
 ###############################################################################
+
+
+def area(lat1, lat2, lon1, lon2, R=6371000):
+    # Radius in meters, so we get area in m^2
+
+    lat1x, lat2x, lon1x, lon2x = np.deg2rad([lat1, lat2, lon1, lon2])
+    result = R**2 * (np.sin(lat1x) - np.sin(lat2x)) * (lon1x - lon2x)
+    return np.abs(result)
+
 ######### PREPPING DATA #######################################################
 
 
@@ -56,9 +67,22 @@ planted_area_wheat = df_area_wheat.query('Period == "YEAR"').groupby('Year')['Va
 
 all_planted_area = planted_area_corn + planted_area_soy + planted_area_wheat
 all_planted_area_rel = all_planted_area / all_planted_area[2010]
-# Production
 
+# Production
 usda_production = pd.read_csv('corn_soy_wheat_production.csv', sep=',', thousands=',').query('Program == "SURVEY"')
+
+# Progress
+df_progress_corn = pd.read_csv('progress_corn.csv', sep=',', thousands=',')
+df_progress_corn.index = pd.to_datetime(df_progress_corn['Week Ending']).values
+df_progress_corn['WeekNr'] = [int(x[-2:]) for x in df_progress_corn['Period']]
+
+df_progress_soy = pd.read_csv('progress_soy.csv', sep=',', thousands=',')
+df_progress_soy.index = pd.to_datetime(df_progress_soy['Week Ending']).values
+df_progress_soy['WeekNr'] = [int(x[-2:]) for x in df_progress_soy['Period']]
+
+# Production and Yield
+df_production = pd.read_csv('corn_soy_production.csv', sep=',', thousands=',')
+df_yield = pd.read_csv('corn_soy_yield.csv', sep=',', thousands=',')
 
 
 # Read HDF file, extract and convert dates
@@ -459,3 +483,181 @@ for aux in dfm.columns:
[…]

### 2018-11-12 quicklook_agriculture.py

@@ -5,10 +5,13 @@ import palettable as pt
 
 
 ##### Make panel plots for various progress reports using a generic function
-def make_panels(df, plotkey, filename, query='', grid=(3,3)):
+def make_panels(df, plotkey, filename, days=True, query='', grid=(3,3)):
 
     dfp = df.query(query)
-    dfp.index = pd.to_datetime(dfp['Week Ending'])
+    if len(dfp['Week Ending'].dropna()) != 0:
+        dfp.index = pd.to_datetime(dfp['Week Ending'])
+    else:
+        dfp.index = pd.to_datetime(dfp['Year'], format='%Y')
 
     fig, axarr = plt.subplots(grid[0], grid[1], figsize=(5,5), dpi=200)
     axarr = axarr.flatten()
@@ -21,8 +24,11 @@ def make_panels(df, plotkey, filename, query='', grid=(3,3)):
             
         ax.set_title(' '.join([y.capitalize() for y in state.split()]))
         for year, df_year in df_state.groupby(df_state.index.year):
-            p = ax.plot(df_year.index.dayofyear, df_year[plotkey])
-            
+            if days:
+                p = ax.plot(df_year.index.dayofyear, df_year[plotkey])
+            else:
+                p = ax.plot(df_year.index.year, df_year[plotkey])
+                
             if i==0:
                 linelist.append(p[0])
                 labellist.append(year)
@@ -39,9 +45,13 @@ df_area_soy = pd.read_csv('area_planted_all_soy.csv', sep=',', thousands=',')
 df_area_wheat = pd.read_csv('area_planted_all_wheat.csv', sep=',', thousands=',')
 
 # Progress
-df_pp_corn = pd.read_csv('progress_corn2.csv', sep=',', thousands=',')
+df_pp_corn = pd.read_csv('progress_corn.csv', sep=',', thousands=',')
 df_pp_soy = pd.read_csv('progress_soy.csv', sep=',', thousands=',')
 df_pp_wheat =  pd.read_csv('progress_wheat.csv', sep=',', thousands=',')
+
+# Production and Yield
+df_production = pd.read_csv('corn_soy_production.csv', sep=',', thousands=',')
+df_yield = pd.read_csv('corn_soy_yield.csv', sep=',', thousands=',')
 
 period = "YEAR"
 start_year = 2010
[…]

### 2018-11-12 sampling_bias.py

@@ -106,7 +106,7 @@ plt.yticks(np.arange(len(lc_percs_ALL)),
 
 plt.ylim(-0.5, 5.5)
 plt.xlabel('Coverage [%]')
-plt.legend()
+plt.legend(fontsize=8)
 plt.savefig('lc_coverage.pdf', bbox_inches='tight')
 plt.close()
 

### 2018-11-16 manuscript/manuscript.tex
Added new plots, wrote new bits

@@
-\documentclass[review, a4paper, 10pt, times]{elsarticle}
+\documentclass[preprint, a4paper, 10pt, times]{elsarticle}
 
@@
 \includegraphics{../corn_soy_planted_sif.pdf}
-\caption{default}
+\caption{Crop planting progess Feb-June.}
 \label{fig:corn_soy_planted_sif}
@@
 
+The SIF radiances do not only reflect the crop status during the growing season.
+Also the total corn and soybean yield for the entire year has an apparent linear relationship with the integrated SIF radiances from June until October (harvest), as can be seen in Figure~\ref{fig:corn_soy_yield_sif}.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{../corn_soy_yield_sif.pdf}
+\caption{Annual crop yield Jun-Oct}
+\label{fig:corn_soy_yield_sif}
+\end{figure}
+
+\subsection{The big TODO list}
+
+\begin{itemize}
+\item Figure 9 and 10 are obviously the most interesting one's, right? Do I want to work out more details on those regressions? Weighted linear regression for the Figure 10?
+\item Do I want/need to show that SIF is better than NDVI/EVI/fluxes/.... ?
+\item My SIF integration periods for Fig 9 and 10 are not arbitrary, but do I need to show robustness against changing the month slightly?
+\item Figures 5 through 8 seem excessive - do I want to take some out?
+\end{itemize}
+
 \section*{}

### 2018-11-16 analysis.py

@@ -492,7 +492,7 @@ dfp_soy = df_progress_soy[df_progress_soy['Data Item'] ==
 
 
 
-
+'''
 # Make 2-D plot of SIF integration months vs CROP WEEK
 corr_max = 0.0
 for sif_integral in range(2,13):
@@ -530,134 +530,225 @@ for sif_integral in range(2,13):
             pass
             # print(sif_integral, crop_week, 'failed')
 
+'''
 
 sif_integral = [5, 5] #[6, 7]
 crop_week = [18, 18]
 plottitle = ['Corn', 'Soybeans']
 markerlist = ['o', '^', 's', '8', '<', 'p', 'D']
 
-fig, axarr  = plt.subplots(1, 2, figsize=(4.5, 2.5), dpi=300)
-for i, (dfp, df_area) in enumerate([(dfp_corn.copy(), df_area_corn.copy()),
-                                    (dfp_soy.copy(), df_area_soy.copy())]):
+for x_key in [SL['abs_755'], 'myd13_evi', 'myd13_ndvi', 'fvc', 'lai']:
+    fig, axarr  = plt.subplots(1, 2, figsize=(4.5, 2.5), dpi=300)
 
-    ax = axarr[i]
-    
-    xdata = []
-    ydata = []
-    lines = []
-    for j, year in enumerate(range(2010, 2017)):
+    print(x_key)
+    print(type(x_key))
+    for i, (dfp, df_area) in enumerate([(dfp_corn.copy(), df_area_corn.copy()),
+                                        (dfp_soy.copy(), df_area_soy.copy())]):
+        
+        ax = axarr[i]
+        
+        xdata = []
+        ydata = []
+        lines = []
+        
+        for j, year in enumerate(range(2010, 2017)):
 
-        sif_data = dfs.loc[dfs.index.year == year, SL['abs_755']]
-        sif_mean = sif_data.mean(axis=1)
-        sif_std = sif_data.std(axis=1)
+            sif_data = dfs.loc[dfs.index.year == year, x_key]
+            
+            if type(x_key) == list:
+                sif_mean = sif_data.mean(axis=1)
+                sif_std = sif_data.std(axis=1)
+            else:
+                sif_mean = sif_data.copy()
+                sif_std = 0 * sif_mean
 
-        for state in np.unique(dfp['State']):
-            this_area = df_area.query(f'Year == {year} & State == "{state}" & Period == "YEAR"')
[…]

### 2019-04-07 manuscript/manuscript.tex
Many updates

--- 2018-11-12 manuscript/manuscript.tex
@@
 \author[uol,nceo]{Peter Somkuti\corref{cor1}\fnref{fn1}}
-\ead{psomkuti@colostate.edu}
+\ead{peter.somkuti@colostate.edu}
 \author[uol,nceo]{Hartmut B\"osch}
-\author[uoe,nceo]{Paul Palmer}
-\author[uoe,nceo]{Liang Feng}
+\author[uoe,nceo-uoe]{Paul I. Palmer}
+\author[uoe,nceo-uoe]{Liang Feng}
 \author[uol,nceo]{Robert Parker}
-\author[nceo]{Tristan Quaife}
+\author[read,nceo]{Tristan Quaife}
 
@@
 \fntext[fn1]{This is the specimen author footnote.}
-\address[uol]{University of Leicester, Department of Physics of Astronomy, Leicester, UK}
+\address[uol]{Department of Physics of Astronomy, University of Leicester, Leicester, UK}
+\address[uoe]{School of Geosciences, University of Edinburgh, Edinburgh, UK}
+\address[read]{University of Reading, Reading, UK}
 \address[nceo]{National Centre for Earth Observation, University of Leicester, Leicester, UK}
-\address[uoe]{University of Edinburgh, Edinburgh, UK}
+\address[nceo-uoe]{National Centre for Earth Observation, University of Edinburgh, Edinburgh, UK}
 
 \begin{abstract}
-This template helps you to create a properly formatted \LaTeX\ manuscript.
+Abstract goes here.
 \end{abstract}
@@
 
-The Greenhouse Gases Observing Satellite (GOSAT) is the first mission solely dedicated to measure atmospheric concentrations of carbon dioxide (CO$_2$) and method (CH$_4$).
-Launched in early 2009 and operated by the Japan Aerospace Exploration Agency (JAXA), GOSAT employs a Fourier-transform spectrometer (TANSO-FTS) to passively measure sunlight back-reflected from the surface of the Earth.
-These hyper-spectral measurements are then used together with appropriate physical models and inversion schemes to retrieve the atmospheric concentration of trace gases like CO$_2$, CH$_4$ and even H$_2$O.
+The Greenhouse Gases Observing Satellite (GOSAT) is the first mission solely dedicated to measure atmospheric concentrations of carbon dioxide (CO$_2$) and methane (CH$_4$).
+Launched in early 2009 and operated by the Japan Aerospace Exploration Agency (JAXA), the Japanese Ministry of Environment (MoE) and the National Institute for Environmental Studies (NIES), GOSAT employs a Fourier-transform spectrometer (TANSO-FTS) to passively measure sunlight back-reflected from the surface of the Earth \citep{yokota2009global}.
+These hyper-spectral measurements are then used together with appropriate physical models and inversion schemes to retrieve the atmospheric concentration of the trace gases.
 
 Due to the high spectral resolution of TANSO-FTS in the O$_2$ A-band at wavelength of $760\:\mathrm{nm}$, several solar (Fraunhofer) lines can be resolved and utilised for the retrieval of SIF.
-We utilise the retrieval method described in \citet{Frankenberg2011}.
-This so-called \textit{physically-based} retrieval is derived from the Fraunhofer line discrimination method, first described in [REF].
-Briefly summarised, the method relies on the fact that any additive radiation originating from the surface will reduce the fractional depth of Fraunhofer lines in the top-of-atmosphere (TOA) spectrum.
+We use the retrieval method described in \citet{Frankenberg2011}.
+This so-called \textit{physically-based} retrieval is derived from the Fraunhofer line discrimination method, first described in \citet{plascyk_fraunhofer_1975}.
+Briefly summarized, the method relies on the fact that any additive radiation originating from the surface will reduce the fractional depth of Fraunhofer lines in the top-of-atmosphere (TOA) spectrum.
 It is therefore possible to decouple reflectance from the additive fluorescence contribution to the total TOA radiance.
-TANSO-FTS records radiances in the shortwave infrared wavelength range in two linear polarization states: P - parallel, and S - perpendicular to the plane of incidence (?
+TANSO-FTS records radiances in the near-visible to shortwave infrared wavelength range in two linear polarization states: P - parallel, and S - perpendicular to the plane of incidence (?
 or is it principal plane?).
@@
 To perform the GOSAT SIF retrievals we employ the University of Leicester Full-Physics algorithm \citep{Cogan2012}, called UoL-FP.
-It derives atmospheric and surface quantities from hyper-spectral measurements via its two components: a full-physics forward model, which accurately models the solar radiation entering and propagating through Earth's atmosphere, its interaction with the surface and finally the finite response at the detector on the space-based platform.
-The forward model calculations are then coupled with the second component of the algorithm: a non-linear inversion scheme that applies the Levenberg-Marquardt modification to the Gauss-Newton method, in order to modify the input parameters of the forward model (the so-called state vector) to match model calculation with real measurements.
+It derives atmospheric and surface quantities from hyper-spectral measurements via its two components: a full-physics forward model, which accurately models the solar radiation entering and propagating through Earth's atmosphere and its interaction with the surface, and the finite response at the detector on the space-based platform.
+The forward model calculations are then coupled with the second component of the algorithm: a non-linear inversion scheme that applies the Levenberg-Marquardt modification to the Gauss-Newton method, in order to modify certain input parameters of the forward model (the so-called state vector) to match model calculation with real measurements.
 Inferring atmospheric and surface quantities as well as quantifying the uncertainty on each retrieved parameter is performed using a Bayesian optimal estimation (OE) framework according to \citet{Rodgers2000}.
 
-We make use of the same processing pipeline which was previously utilized for the generation of high-quality atmospheric trace gas data sets \citep{Buchwitz2017,Trent2018} at the University of Leicester, using the same core retrieval algorithm.
+We make use of the same processing pipeline which was previously used for the generation of high-quality atmospheric trace gas data sets (e.g.
+\citet{Buchwitz2017,Trent2018}) at the University of Leicester, using the same core retrieval algorithm.
 On a per-scene (measurement) basis, the surface pressure is informed by the ECMWF ERA-Interim model, and the surface albedo is estimated through the measured radiances themselves assuming a Lambertian surface model.
 
-Following the retrieval strategy in \citet{Frankenberg2011}, we retrieve SIF at two micro-windows at $755\:\mathrm{nm}$ ($755.86 - 758.95$ nm) and $772\:\mathrm{nm}$ ($769.59 - 774.83$ nm), as well as the two polarizations, independently.
+We retrieve SIF at two micro-windows at $755\:\mathrm{nm}$ ($755.86 - 758.95$ nm) and $772\:\mathrm{nm}$ ($769.59 - 774.83$ nm), as well as the two polarizations, independently, using \citet{Frankenberg2011}.
 For both retrieval windows, the SIF radiances are represented by a constant additive offset to the TOA radiances, along with a linear surface albedo (constant + slope), and instrument dispersion shift and stretch.
 As there are weak oxygen lines present in the $772\:\mathrm{nm}$ window, surface pressure is additionally retrieved in that micro-window.
-To exclude any scenes with large cloud contamination, we ran a cloud-screening algorithm beforehand.
+We excluded any scenes with large cloud contamination by using a cloud-screening algorithm beforehand.
 Only those GOSAT scenes are processed where the apparent surface pressure deviated by less than $100\:\mathrm{hPa}$ from the ERA-Interim prediction.
+The comparatively large surface pressure deviation threshold is possible due to SIF retrievals being less sensitive to cloud contamination of the scene \citep{frankenberg2012remote}.
 
 A crucial step in the SIF retrieval process is the bias correction.
-As established by \citet{Frankenberg2011}, small non-linearities in the analogue-to-digital conversion of the TANSO-FTS interferograms lead to the same fractional reduction of Fraunhofer lines as any SIF signal would do and thus result in unphysical SIF values.
+Small non-linearities in the analogue-to-digital conversion of the TANSO-FTS interferograms lead to the same fractional reduction of Fraunhofer lines as any SIF signal would do and thus result in unphysical SIF values.
 In order to rid the measurements of these instrument artefacts, the retrieved SIF values need to be corrected.
-To achieve the bias correction, we apply a slightly different method compared to \citet{Frankenberg2011}.
+To achieve the bias correction, we use a slightly different method compared to \citet{Frankenberg2011}.
 First, we use the ESA CCI Land Cover map v2.0.7 \citep{Bontemps2013} to obtain the land cover classes for the surfaces seen by each GOSAT measurement (see Section~\ref{sec:collocation}).
 To identify footprints which can be assumed to be permanently free of vegetation, we consider only surfaces where at least $95\%$ of all land cover-class pixels within the footprint belong to the types: urban, desert, snow and ice, or any bare type.
-This approach has the advantage that not only highly reflective surfaces like ice shields or deserts are used for the correction process, but also darker surfaces such as mountainous regions.
+This approach has the advantage that highly reflective surfaces like ice shields or deserts are used for the correction process, and also darker surfaces such as mountainous regions.
 
-The calibration curve is produced via the relationship between retrieved offset ($z_0$) and the mean radiance in the entire first GOSAT band ($\overline{I}_1$).
-Ideally, this curve would be flat, centered around zero, however the instrumental artefacts lead to a somewhat complicated shape, as shown in Figure XX [should I put a figure here?
+We produce calibration curves via the relationship between retrieved offset ($z_0$) and the mean radiance in the entire first GOSAT band.
+Ideally, this curve would be flat and centered around zero, however the instrumental artefacts lead to a somewhat complicated shape, as shown in Figure XX [should I put a figure here?
 or is this too technical already..].
-As this bias is of purely instrumental nature, it is not necessarily safe to assume that the bias remained the same over the long operational time of the instrument.
-Thus, we adopt three different strategies to correct for this instrumental bias.
+This instrumental bias varies over time and requires a time-dependent correction.
+Consequently, we adopt three different strategies to correct for this instrumental bias.
 For the first one, we collect retrievals over non-fluorescing areas in seasonal aggregates (DJF, MAM, JJA, SON).
-For every season in every year the SIF retrievals are being corrected according to the calibration curve derived at that particular season-year combination.
+For every season in every year, we correct the SIF retrievals according to the calibration curve derived at that particular season-year combination.
 The second strategy is similar, the only difference being that retrievals for an entire year are collected.
@@
 \item MODIS/Aqua MYD13C1 V006 Vegetation Indices ($0.05^\circ$ resolution, $2010-2016$) \citep{MYD13C1}
-\item MODIS/Aqua MYD11C2 V006 Land Surface Temeprature ($0.05^\circ$ resolution, $2010-2016$) \citep{MYD11C2}
+\item MODIS/Aqua MYD11C2 V006 Land Surface Temperature ($0.05^\circ$ resolution, $2010-2016$) \citep{MYD11C2}
 \item SPOT/VEGETATION Leaf Area Index V2.0.1 ($1\:\mathrm{km}$ resolution, $2010-2016$)
@@
 
-\subsection{GOSAT Sampling Bias}
+\subsection{GOSAT sampling bias}
 \label{sec:sampling_bias}
@@
 As mentioned during the discussion on GOSAT SIF retrievals (Section~\ref{sec:GOSAT_SIF}), the FTS instrument, due to its pointing strategy/nature, causes potential sampling biases due to the pointing locations.
-While there is an inherent bias due to clouds, as GOSAT SIF retrievals can not be performed in the presence of thick clouds, the sampling strategy results in non-uniform selection of surfaces throughout the region of interest (ROI).
-Illustrated in Figure~\ref{fig:sampling}, the sampling density is shown for the entire time period from the beginning of $2010$ until the end of $2016$.
+While there is an inherent bias due to clouds, as GOSAT SIF retrievals can not be performed in the presence of thick clouds, the sampling strategy results in non-uniform selection of surfaces throughout the region of interest (ROI) which covers the US states North Dakota (ND), South Dakota (SD), Kansas (KS), Nebraska (NE), Minneapolis (MN), Iowa (IA), Missouri (MO), Wisconsin (WI) and Illinois (IL).
+Figure~\ref{fig:sampling} shows the sampling density is shown for the entire time period from the beginning of $2010$ until the end of $2016$.
 
@@
 \includegraphics{../coverage_map.png}
-\caption{Land cover classes (left) and GOSAT sampling density shown for the region of interest ($104$W - $87.5W$, $37$N - $49$N).
+\caption{Land cover classes (left) and GOSAT sampling density (right) shown for the region of interest ($104$W - $87.5$W, $37$N - $49$N).
 Yellow land cover pixels correspond to crop, orange represents grassland, green-colored pixels are various tree types, and red areas are urban regions.
@@
 
-The question arises, whether the sampling of the various surfaces of the chosen region of interest is representative of the entire area.
+The question arises, whether the sampling of the various surfaces of the chosen ROI is representative of the entire area.
 To that end, we compare the most common land cover classes (Figure~\ref{fig:sampling} left) of the entire region of interest at the native resolution ($300\:\mathrm{m}$) of the ESA CCI Land Cover data set (excluding water bodies) to the sub-pixel aggregated data at the location of the GOSAT footprints.
@@
 \includegraphics{../lc_coverage.pdf}
-\caption{default}
+\caption{Comparison of overall land cover coverage between the entire ROI and GOSAT sampling.}
 \label{fig:lc_coverage}
@@
 For the total period, GOSAT is well representing the overall composition of land cover classes of the region of interest.
-The largest differences are seen for flooded tree cover, where GOSAT is slightly over-repensenting ($+1.69\%$), and grassland, where GOSAT is under-representing ($-3.25\%$).
+The largest differences are seen for flooded tree cover, where GOSAT is slightly over-representing ($+1.7\%$), and grassland, where GOSAT is under-representing ($-3.3\%$).
 
@@
 
+As we are interested mainly in the response of crops (corn, soy), only GOSAT measurements that cover at least $50\%$ any cropland-type surface were kept for the subsequent analysis.
+
 \begin{figure}[htbp]
@@
 \includegraphics{../lc_diff_monthly.pdf}
-\caption{Jan 2015 has not been taken into account due to the low number of measurements in that month.}
+\caption{The monthly differences between LC coverage of the entire ROI and the LC coverage as seen by GOSAT.
+January 2015 has not been taken into account due to the low number of measurements in that month.}
 \label{fig:lc_diff_monthly}
@@
 
-\subsection{Time Series}
+\subsection{SIF time series}
 \label{sec:SIF_TS}
@@
 The SIF retrievals are aggregated on a monthly basis, where the mean of all measurements inside the ROI for a given month are considered.
-As we have two different polarisations (P, S) and three different calibration procedures (seasonal, annual, spline-based), there are a total of six SIF time series.
-Figure~\ref{fig:sif_ts} shows this ensemble of SIF data, where the thick line is the median of all six time series, and the shaded area visualizes the minimum and maximum value of the given month to show the spread of the ROI-averaged SIF.
-It should be noted that the variability in the SIF time series stems mostly from the two different polarisations, rather than the calibration methodology.
-Months with less than $200$ measurements are dropped from both the visualization and the analysis, which affects only January $2015$, a month in which GOSAT was only partially operative due to instrumental issues.
+As we have two different polarizations (P, S) and three different calibration procedures (seasonal, annual, spline-based), there are a total of six SIF time series.
+Figure~\ref{fig:sif_ts} shows this ensemble of SIF data, where the thick line is the median of all six time series.
+The bottom panel shows the anomalies, and the shaded area visualizes the respective minimum and maximum value of the given month to show the spread of the ROI-averaged SIF.
+We find that the variability in the six SIF time series stems mostly from the two different polarizations, rather than the calibration methodology.
+Months with less than $100$ measurements are dropped from both the visualization and the analysis, which affects only December $2012$ and January $2015$, months in which GOSAT was only partially operative due to instrumental issues.
 
@@
 \includegraphics{../SIF_overview.pdf}
-\caption{default}
+\caption{The SIF time series (top panel) and corresponding anomaly plot (bottom panel).
+In the top panel, the green line represents the median of the six monthly-averaged SIF time series (two polarization states, three bias correction schemes), while the blue-dashed line represents the measurement count per month.
+The dotted lines in the bottom plot mark the $2\sigma$ and $3\sigma$ values of the anomalies.}
 \label{fig:sif_ts}
@@
 The anomalies in Figure~\ref{fig:sif_ts} (bottom) are calculated as the difference between the current month and the median of all of the same months over the seven-year period.
-While the straight time series does not immediately reveal any striking features, the anomalies show several important ones.
-First, it is clear that over this relatively short period of seven years, the number of anomalous months within that period somewhat large: counting the number of months where the SIF signal exceeds the standard deviation of all anomalies (dotted green lines in Fig.~\ref{fig:sif_ts}, ), one arrives at $22$ (or $26\%$) anomalous months.
-We conclude that this short time period does not have a strong baseline, as every year has at least two anomalous months.
-[REFERENCE WOLF LIU AND OTHERS AND POINT OUT THAT THEY USED A SIMPLE BASELINE] It is therefore imperative to look at every anomaly within the context of other climatological and agricultural drivers.In chronological order, the big anomalies can be easily identified and related to known meteorological events.
+While the time series itself does not immediately reveal any striking features, the anomalies show several important ones.
+Given this relatively short period of seven years, only one month shows an anomalous value beyond $3\sigma$ (five months beyond $2\sigma$).
+We conclude that this short time period does not have a strong baseline, as most years have one ore more anomalous months.
+[REFERENCE WOLF LIU AND OTHERS AND POINT OUT THAT THEY USED A SIMPLE BASELINE] It is therefore imperative to look at every year and potential anomaly within the context of other climatological and agricultural drivers.
+In chronological order, they can be easily identified and related to known meteorological events.
 
-Starting in $2010$, we see the effects of the rapid El Ni\~no-La Ni\~na transition, which brought excessive rain to the Corn Belt in the summer months (Fig.~\ref{fig:anomalies_0} bottom row) and drove plant growth.
+Starting in $2010$, we see the effects of the rapid El Ni\~no-La Ni\~na transition, which brought excessive rain to the Corn Belt in the summer months (Fig.~\ref{fig:anomalies_0} second row) and drove plant growth \citep{USDA2010}.
 
-In $2011$, we see a negative anomaly for spring, despite average precipitation and temperatures for that season.
-The reason for the negative anomaly is hinted at by the positive GRACE anomaly for $2011$ (Fig.~\ref{fig:anomalies_0} middle row).
+In $2011$, we see a small negative anomaly for spring, despite average precipitation and temperatures for that season.
+The reason for the negative anomaly is hinted at by the positive GRACE anomaly for $2011$ (Fig.~\ref{fig:anomalies_0} top row).
 Large amounts of melting snow in the northern Corn Belt, as well as high precipitation in the south eastern corner (Missouri) have caused massive flooding of the Mississippi and Missouri rivers.
-As most parts of the ROI have not seen any increased rainfall, the anomaly plot in Figure~\ref{fig:anomalies_0} (bottom) does not show any significant outlier.
+As most parts of the ROI have not seen any increased rainfall, the precipitation anomaly plot in Figure~\ref{fig:anomalies_0} (second row) does not show any significant outlier.
 The flooded areas, however, are visible as a positive anomaly in the GRACE data.
-The flooding has not only delayed planting progress, but also SOMETHING
+While many farmers in the Mississippi River Valley were affected by planting delays due to levee breaches \citep{olson2012impacts} (maybe need better / more references to this), regions like Iowa, Nebraska and Kansas were not as severely impacted, hence the smaller anomaly.
 
-The two anomalies in $2012$ are the most well-known and most-studied ones.
-In short, a warm winter and warm spring (see LST anomalies in Fig.~\ref{fig:anomalies_2} top) caused early and fast vegetation growth.
-In the following summer, however, anomalously low precipitation (Fig.~\ref{fig:anomalies_0} bottom) was responsible for drought conditions.
+The two anomalies in $2012$ are the most well-known and most-studied ones (e.g.
+\citet{wolf2016warm}).
+In short, a warm winter and warm spring (see LST anomalies in Fig.~\ref{fig:anomalies_0} third row) caused early and fast vegetation growth.
+In the following summer, however, anomalously low precipitation (Fig.~\ref{fig:anomalies_0} second row) was responsible for drought conditions.
 As a consequence of the early spring onset due to warm temperatures, the plants used up soil water reserves quicker and depleted the soil of moisture, thus exacerbating the drought even further.
 This $2012$ drought was one of the most severe droughts in recorded history, with conditions comparable to the $1930$'s dustbowl era.
-The drought conditions are seen equally strongly in the soil moisture (Fig.~\ref{fig:anomalies_2} middle and bottom) anomalies [WHY IS PASSIVE NOT AS NICE HERE?], as well as the GRACE anomalies (Fig.~\ref{fig:anomalies_0} middle).
+The drought conditions are seen equally strongly in the soil moisture (Fig.~\ref{fig:anomalies_0} last row) anomalies, as well as the GRACE water storage anomalies (Fig.~\ref{fig:anomalies_0} top row).
 
@@
 In the spring months, high precipitation and cool temperatures delayed the planting process - corn seed planting is generally done on warm and dry days - as well as caused slow maturing of crops.
-[POINT TO USDA GRAPHS].
 
 The following two years exhibit positive SIF anomalies.
-In $2015$, near-ideal temperatures and favourable rainfall have led to good growing an maturing conditions for corn and soybeans, despite the rainfall distribution being suboptimal - the southern and eastern regions of the Corn Belt experienced more excessive rain.
+In $2015$, near-ideal temperatures and favorable rainfall have led to good growing an maturing conditions for corn and soybeans, despite the rainfall distribution being suboptimal - the southern and eastern regions of the Corn Belt experienced more excessive rain.
 $2016$ proved to be an even better year for crop production than $2015$, and this is reflected in the SIF anomaly.
-After an intense El Ni\~no in $2015$, the quick transition to a weak La Ni\~na, and a fairly wet summer has provided ideal conditions for crops.
+After an intense El Ni\~no in $2015$, the quick transition to a weak La Ni\~na, and a wet summer has provided ideal conditions for crops.
+
+A short summary is given in Table~\ref{tbl:anomaly_table}.
 
@@
 \includegraphics{../anomalies_755_abs_0_median.pdf}
-\caption{default}
+\caption{Anomalies of GRACE water equivalent thickness (cm), precipitation, land surface temperature and soil moisture (all in blue), along with SIF anomalies (dashed, green).}
 \label{fig:anomalies_0}
 \end{figure}
+
+%\begin{figure}[htbp]
+%\centering
+%\includegraphics{../anomalies_755_abs_2_median.pdf}
+%\caption{default}
+%\label{fig:anomalies_2}
+%\end{figure}
+
+%\begin{figure}[htbp]
+%\centering
+%\includegraphics{../anomalies_755_abs_1_median.pdf}
+%\caption{default}
+%\label{fig:anomalies_1}
+%\end{figure}
+
+\begin{table}[htp]
+\begin{center}
+\begin{tabular}{c|c|l}
+Year & Anomaly & Details \\
+\hline
+$2010$ & $+$   & Quick El Ni\~no-La Ni\~na transition, \\
+             & & high precipitation during summer \\
+$2011$ & $-$   & Snow melt caused flooding, delaying planting \\
+             & & in some areas of the Corn Belt (NM, SD, ND, WI) \\
+$2012$ & $+/-$ & Warm spring induced early onset, \\
+             & & summer drought collapsed yield \\
+$2013$ & $-$   & Cold and wet spring delayed planting \\
+$2014$ & $-$   & -same- \\
+$2015$ & $+$   & Good planting and growing conditions, \\
+             & & despite large rainfall due to El Ni\~no \\
+$2016$ & $+$ & Weak La Ni\~na/wet summer for good conditions \\
+\end{tabular}
+\end{center}
+\label{tbl:anomaly_table}
+\caption{Summary of the SIF anomalies and their causes.}
+\end{table}%
+
+\subsection{Flux inversion}
+
+SIF is intrinsically linked to primary production (GPP) as it is a by-product of the photosynthetic process that ultimately leads to carbon fixation.
+As such, the relationship between SIF and GPP has been explored early on when global-scale retrievals of SIF were performed \citep{Frankenberg2011,Guanter2012}.
+The SIF-GPP relationship has been described as linear when averaged on regional scale and with time, with a potential dependence on biome.
+Recent studies, however, have shown that the SIF-GPP relationship can change significantly when plants are undergoing stress, such as from a drought \citep{Wieneke2018,Wohlfahrt2018}.
+
+We compare gross flux anomalies from CASA, as well as net flux anomalies obtained through the inversion of GOSAT XCO$_2$ measurements (see Section~\ref{sec:fluxes}) to the SIF anomalies.
+Figure~\ref{fig:anomalies_3} shows that the large drought event of 2012 is represented in both gross and net fluxes - several other anomalies (2010, 2011, 2015) are also well-represented in both flux data.
 
@@
 \includegraphics{../anomalies_755_abs_2_median.pdf}
-\caption{default}
-\label{fig:anomalies_2}
-\end{figure}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{../anomalies_755_abs_1_median.pdf}
-\caption{default}
-\label{fig:anomalies_1}
-\end{figure}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{../anomalies_755_abs_3_median.pdf}
-\caption{default}
+\caption{Flux anomalies [gC/m$^2$/yr] overlaid on top of SIF anomalies [W/m$^2$/sr/$\mu$m].}
 \label{fig:anomalies_3}
@@
 
-\section{Crop planting and yield}
+\subsection{Crop planting and yield}
 
 The US Corn Belt is a very specific type of biome.
-As recently investigated by \citet{Alter2017}, it even generates its own climate.
-Despite the ROI being almost $1800 \cdot 10^9\;\mathrm{m}^2$ ($\approx 440$ million acres) in area, almost half of it is managed cropland.
-Meteorological conditions are thus not the only factor in determining the onset and productivity of one given season.
-It was pointed out in Section~\ref{sec:SIF_TS} that certain for years, the rainfall amount in springtime have caused delays in the planting of crops.
-To show that SIF indeed captures the delays in planting, we compare against the USDA crop progress reports.
+As recently investigated by \citet{Alter2017}, it even generates its own climate, with the agricultural intensification resulting in cooler temperatures and increased rainfall.
+Despite the ROI being almost $1800 \times 10^9\;\mathrm{m}^2$ ($\approx 440$ million acres) in area, around half of it is irrigated cropland.
+Meteorological conditions are thus not the only factor in determining the vegetation onset and productivity of one given season.
+It was pointed out in Section~\ref{sec:SIF_TS} that for certain years, the rainfall amount in springtime have caused delays in the planting of crops.
+To show that SIF indeed captures the delays in planting, we compare against the USDA crop progress reports \citep{USDA2010,USDA2011,USDA2012,USDA2013,USDA2014,USDA2015,USDA2016}.
 In these reports, the percentage of acreage planted is recorded based on farmer surveys.
-We translate these state-wide and weekly data for the whole ROI by multiplying with the total planted area for that given year and state in order to obtain an effective "planted area".
-We compare this number for every year against the integrated SIF radiances from Feburary onwards to June.
+We translate these weekly state-wide data for the whole ROI by multiplying with the total planted area for that given year and state in order to obtain an effective "planted area".
+We compare this number for every year against the integrated (or cumulative) SIF radiances (monthly ROI averages) from February onwards to June.
 
@@
 \includegraphics{../corn_soy_planted_sif.pdf}
-\caption{default}
+\caption{Crop planting progress (1 acre $\approx 4047$ m$^2$) at week 18 as a function of time-integrated monthly SIF radiances from February to June.
+Uncertainty bars for SIF is the standard error on the 6 different SIF time series.
+Low values for the years $2013$ and $2014$ are the result of planting delays due to rainfall and cold temperatures (see Section \ref{sec:SIF_TS}).}
 \label{fig:corn_soy_planted_sif}
@@
 
+The SIF radiances do not only reflect the crop status during the growing season.
+Also the total corn and soybean yield for the entire year has an apparent linear relationship with the integrated SIF radiances from June until October (harvest), as can be seen in Figure~\ref{fig:corn_soy_yield_sif}.
+The record-low yield due to the 2012 drought is highly apparent in the figure, also making it clear that a yield prognosis based on planting progress alone (Fig.~\ref{fig:corn_soy_planted_sif}) is not feasible.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{../corn_soy_yield_sif.pdf}
+\caption{Annual crop yield (1 bushel corn $\approx 25.4$ kg, 1 bushel soybean $\approx 27.2$ kg) from June to October as a function of the time-integrated monthly SIF radiances from June to October.
+The uncertainty bars for crop yield is the standard error of all nine states within the ROI, however that number is not taken into account for the linear regression.
+The value in the bracket within the regression equation is the uncertainty of the fitted slope and offset.}
+\label{fig:corn_soy_yield_sif}
+\end{figure}
+
+The observed good relationship between SIF, and crop planting and crop yield is not particularly surprising, given the good correlation between SIF and NDVI/EVI time series anomalies ($r > 0.6$, not pictured).
+The predictive power of hyperspectral indices from remote sensing instruments in characterising crop yield has been demonstrated in the past, such as by \citet{Shanahan2001}, \citet{Prasad2006}, \citet{Beckerreshef2010} and \citet{Mkhabela2011}.
+Even in the case of the entire Corn Belt, NDVI/EVI remain better predictors than SIF for both planting ($r = 0.88$ / $r = 0.86$ for corn) and yield ($r = 0.98$ / $r = 0.96$ for corn).
+Similarly good predictors are leaf area index (LAI) and fractional vegetation cover (FVC) with $r = 0.92$ and $r = 0.90$ for corn planting, and $r = 0.98$ and $r = 0.98$ for corn yield.
+The better performance of NDVI/EVI as well as LAI and FVC most likely stem from the noisy nature of the SIF data (see Section \ref{sec:GOSAT_SIF}).
+Even at the scale of the ROI, monthly values of the ROI-averaged SIF can have an attached uncertainty of at least $\approx 20\%$ (estimated through sub-regional aggregation).
+
+A potential weakness regarding the relationship between SIF and crop yields is the following.
+We cannot simply deduce from the SIF measurements alone, whether GOSAT is observing stronger SIF due to the photosynthetic response of crops, or whether GOSAT is merely seeing larger amounts of vegetated area.
+To exclude this possibility, we construct three control time series to compare against the results seen in Figure~\ref{fig:corn_soy_yield_sif}.
+
+The first control is to look at the relationship between total planted area in the nine states against crop yield, where the planted area and yield values are separate for each crop.
+We see a positive correlation for soybeans ($r = 0.61$), whereas for corn, there is a surprising negative and weak correlation ($r = 0.27$).
+This negative correlation for corn is solely due to the year 2012, removing that one data point reduces the correlation coefficient to $r = 0.00$, which is already hinted by the large p-value of $0.23$.
+The positive and significant correlation for soybeans is explained through both the steadily increasing yields together with a general increase in soybean planting.
+The USDA projects soybeans to reach similar levels to corn in terms of amount of planted acres in the near future \citep{USDA-prognosis}.
+We cannot distinguish whether a specific GOSAT footprint covered a soy field or a corn field (or any other crop) at the time of measurement.
+Hence we can not completely reject the possibility that the SIF signal we see in Figure~\ref{fig:corn_soy_yield_sif} is due to mainly covering soybean fields.
+Since most farmers in the Corn Belt practice individual crop rotation between corn and soybeans \citep{suyker2012gross}, it is most likely that we are sampling a mix between corn, soybeans, and to a lesser extent, wheat.
+We therefore assume that the SIF-yield relationship is not driven due to sampling that is heavily weighted towards soybean fields.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{../corn_soy_yield_TOTAL_PLANTED.pdf}
+\caption{Crop yield versus the total planted area in that year, with planted area vales for the specific crop.}
+\label{fig:corn_soy_yield_TOTAL_PLANTED}
+\end{figure}
+
+The second control relies on a similar idea, however focuses on satellite-derived vegetation data.
+We aggregate the NDVI grid boxes ($0.05^\circ$ resolution) in the ROI, which according to the ESA CCI LC map have at least $5\%$ of rainfed cropland land cover classes.
+For every year between 2010 and 2016, an NDVI map is then created in which every grid cell contains the maximal NDVI value for that year.
+Finally, the fraction of grid cells which exhibit an NDVI value above $0.3$ is calculated.
+A value of $0.3$ is a low enough threshold that should discriminate between a vegetated and non-vegetated surface.
+This provides a first order estimate of the number of grid cells that have some level of vegetation in them.
+As seen in Fig.~\ref{fig:corn_soy_yield_VI_FRACTION}, this fraction of vegetated area (reduced to crop-covered pixels within the ROI) does not provide a better correlation with crop yields as SIF or vegetation indices themselves.
+What this analysis shows, however, is that practically every grid cell ($>98\%$) covering crop fields has been vegetated at some point during the year.
+Both correlation coefficients are statistically not significant with $p > 0.1$, mainly due to the fact that the NDVI fraction only changes by about $1\%$.
+Compared to Figure~\ref{fig:corn_soy_yield_TOTAL_PLANTED}, we cannot distinguish whether a pixel belongs to a corn or soybean field, and hence cannot split the NDVI fraction into corn and soy components.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{../corn_soy_yield_VI_FRACTION.pdf}
+\caption{Crop yield vs the fraction of valid NDVI pixels $> 0.3$.
+The correlation coefficients $r > 0.4$ suggest that the annual crop yield is weakly related to the total area of tilled fields for both corn and soybean crops.}
+\label{fig:corn_soy_yield_VI_FRACTION}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{../ndvi_crop/2012_VI_11_maximum.pdf}
+\caption{THIS IS A DEBUG PLOT - DELETE ME.
+2012 all NDVI grid cells that are over $5\%$ crop LC.
+This shows the max NDVI of 2012.
+Apart from eastern Colorado, the rest of the ROI (valid crop pixels) is vegetated at some point in the year.}
+\label{fig:debug1}
+\end{figure}
+
+For the third control, we investigate a potential sampling bias.
+Already shown in Figure~\ref{fig:lc_diff_monthly}, there is a variability in terms of the surfaces sampled by GOSAT, mostly a result of changing cloud cover and sampling strategy.
+We compare the crop yield to the fraction of cropland (as determined by the ESA CCI LC map) that all GOSAT soundings see in a given year.
+Here we use the same set of soundings that was pre-filtered beforehand, so only individual soundings are considered that cover more than $50\%$ of the crop type land cover type.
+The observed correlation at $r < 0.46$ is weaker than in Figure~\ref{fig:corn_soy_yield_VI_FRACTION} ($r > 0.75$), and neither relationship is statistically significant ($p > 0.15$).
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{../corn_soy_yield_LC_FRACTION.pdf}
+\caption{Crop yield vs the total fraction LC crop type surface seen in a given year.}
+\label{fig:corn_soy_yield_LC_FRACTION}
+\end{figure}
+
+Despite the fact that two of the three controls (Fig.~\ref{fig:corn_soy_yield_VI_FRACTION} and \ref{fig:corn_soy_yield_LC_FRACTION}) exhibit a moderate correlation with crop yields, the SIF radiances show a much higher one.
+We thus conclude that GOSAT SIF (and vegetation indices) does not merely track whether a surface was vegetated, but can also provide information on the vegetation density and yield through the intensity of the signal.
+
+\section{Conclusions}
+
 \section*{}

### 2019-04-07 analysis.py

@@ -16,6 +16,8 @@ import numpy as np
 import pandas as pd
 from netCDF4 import num2date, Dataset
 
+import statsmodels.api as sm
+
 import scipy as sp
 from scipy import stats as sps
 from scipy.interpolate import RegularGridInterpolator as RGI
@@ -23,6 +25,8 @@ import itertools
 
 import palettable as pt
 import statsmodels.formula.api as smf
+
+from IPython import embed
 
 from bbox import *
 
@@ -33,7 +37,7 @@ from bbox import *
 resample = 'MS'
 rs_apply = 'mean'
 min_sif = 0.0
-min_count = 200
+min_count = 100
 min_date = '20100101'
 max_date = '20161231'
 anomaly_stat = 'median'
@@ -84,6 +88,8 @@ df_progress_soy['WeekNr'] = [int(x[-2:]) for x in df_progress_soy['Period']]
 df_production = pd.read_csv('corn_soy_production.csv', sep=',', thousands=',')
 df_yield = pd.read_csv('corn_soy_yield.csv', sep=',', thousands=',')
 
+# Quality
+df_quality_corn = pd.read_csv('quality_all_corn.csv', sep=',', thousands=',')
 
 # Read HDF file, extract and convert dates
 h5 = h5py.File('fluorescence_subset.h5', 'r')
@@ -92,16 +98,89 @@ dates = num2date(h5['frac_days_since'][:], units='days since 1970-01-01')
 # Create dataframe using the dates, and then read all 1-dim data arrays into it
 df = pd.DataFrame(index=dates)
 
+# Grab the land cover data, and only keep those we want?
+lccs = h5['lccs_fraction'][:]
+lc_filter = (lccs[:,2] + lccs[:,6]) >= 0.50
+
 print("Reading HDF")
 for key in h5.keys():
     if len(h5[key].shape) == 1:
         if h5[key].shape[0] == len(h5['Exposure_id']):
             # Don't want the empty 'simple' fields
             if 'simple' in key: continue
-            
+
             #print(f"Reading {key}")
-            df[key] = h5[key][:] #[qual]
+            df[key] = h5[key][:]
 print("Done")
+
+
+
+vi_fraction = pd.Series(index=np.arange(2010, 2017))
+planted_total = pd.Series(index=np.arange(2010, 2017))
[…]

### 2019-04-07 quicklook_agriculture.py

@@ -53,6 +53,9 @@ df_pp_wheat =  pd.read_csv('progress_wheat.csv', sep=',', thousands=',')
 df_production = pd.read_csv('corn_soy_production.csv', sep=',', thousands=',')
 df_yield = pd.read_csv('corn_soy_yield.csv', sep=',', thousands=',')
 
+# Quality
+df_status_corn = pd.read_csv('quality_all_corn.csv', sep=',', thousands=',')
+
 period = "YEAR"
 start_year = 2010
 end_year = 2016
@@ -164,3 +167,9 @@ make_panels(df_pp_wheat[df_pp_wheat['Data Item'] == "WHEAT, SPRING, DURUM - PROG
 make_panels(df_pp_wheat[df_pp_wheat['Data Item'] == "WHEAT, SPRING, (EXCL DURUM) - PROGRESS, MEASURED IN PCT PLANTED"],
             'Value', 'spring_wheat_progress.pdf',
             query='(Commodity == "WHEAT") & (Year > 2009) & (Year < 2017)')
+
+for status in ['VERY POOR', 'POOR', 'FAIR', 'GOOD', 'EXCELLENT']:
+    make_panels(df_status_corn[df_status_corn['Data Item'] == f"CORN - CONDITION, MEASURED IN PCT {status}"],
+                'Value', f'corn_status_{status}.pdf',
+                query='(Commodity == "CORN") & (Year > 2009) & (Year < 2017)')
+

### 2019-04-07 sampling_bias.py

@@ -2,6 +2,8 @@
 #matplotlib.use('agg')
 
 from matplotlib import rcParams
+import matplotlib.patheffects as PathEffects
+
 
 rcParams['font.family'] = 'serif'
 rcParams['font.serif'] = ['Times', 'Times New Roman']
@@ -161,15 +163,19 @@ for year in range(2010, 2017):
 # Set this month to NaN's as we don't use it anyway
 df_diff.loc['2015-01-01'] = np.nan
 # Monthly deviation of LC coverage
-fig = plt.figure(figsize=(4, 2), dpi=300)
+fig = plt.figure(figsize=(3, 2), dpi=300)
 
 for x in lc_sort_ALL[:3]:
     (df_diff[f'gosat_{x}'] - df_diff[f'all_{x}']).plot(label=lc_labels[x])
-fig.legend(bbox_to_anchor=(1.45, 0.85), ncol=1, fontsize=7)
+fig.legend(bbox_to_anchor=(1.65, 0.85), ncol=1, fontsize=7)
 #fig.subplots_adjust(right=1.25)
 fig.tight_layout()
 plt.ylabel("LC coverage difference [$\%$]")
 plt.xlabel("Year")
+xmin, xmax = plt.gca().get_xlim()
+plt.hlines([0], xmin=xmin, xmax=xmax, linestyle='dashed',
+           color='grey', lw=0.5)
+plt.xlim(xmin, xmax)
 plt.savefig('lc_diff_monthly.pdf', bbox_inches='tight')
 plt.close()
         
@@ -208,17 +214,56 @@ for p_idx in [1,2]:
                             linestyle='-', linewidth=0.5)
     states.set_rasterized(True)
 
+
     if p_idx == 1:
-        
+
         ax.pcolormesh(lccs_lon, lccs_lat, lccs_box[::1,::1],
                       cmap=cmap, norm=norm,
                       #extent=[lon_min, lon_max, lat_min, lat_max],
                       #origin='upper',
                       transform=ccrs.PlateCarree(),
                       rasterized=True)
-        
+
+
+
+        txt = ax.text(-100.0, 47.5, "ND", ha='center', va='center',
+                transform=ccrs.PlateCarree())
+        txt.set_path_effects([
+            PathEffects.withStroke(linewidth=1, foreground='w')])
+        txt = ax.text(-101.0, 44.75, "SD", ha='center', va='center',
+                transform=ccrs.PlateCarree())
+        txt.set_path_effects([
[…]

### 2019-04-23 manuscript/manuscript.tex
Updates

@@
 To identify footprints which can be assumed to be permanently free of vegetation, we consider only surfaces where at least $95\%$ of all land cover-class pixels within the footprint belong to the types: urban, desert, snow and ice, or any bare type.
-This approach has the advantage that highly reflective surfaces like ice shields or deserts are used for the correction process, and also darker surfaces such as mountainous regions.
+This approach has the advantage that highly reflective surfaces like ice shields or deserts are used for the correction process, as well as darker surfaces such as mountainous regions.
 
@@
 Yellow land cover pixels correspond to crop, orange represents grassland, green-colored pixels are various tree types, and red areas are urban regions.
-In the right picture, all GOSAT soundings for the entire time period $2010-2016$ are collected and visualized as a density map to illustrate the both sparse and irregular sampling pattern.}
+In the right picture, all GOSAT soundings for the entire time period $2010-2016$ are collected and visualized as a density map (red indicates higher sounding density) to illustrate the both sparse and irregular sampling pattern.}
 \label{fig:sampling}
@@
 
-Repeating the same analysis on a monthly basis, a different picture than Figure~\ref{fig:lc_coverage} can arise, as GOSAT's sampling is not only non-uniform geographically, but also changed over time.
+Repeating the same analysis on a monthly basis, a different picture than Figure~\ref{fig:lc_coverage} can arise, as GOSAT's sampling is not only non-uniform geographically, but also changes over time.
 In Figure~\ref{fig:lc_diff_monthly}, the differences between GOSAT-seen and total ROI land cover class coverage for monthly aggregates is shown for the three most prevalent classes.
@@
 
-As we are interested mainly in the response of crops (corn, soy), only GOSAT measurements that cover at least $50\%$ any cropland-type surface were kept for the subsequent analysis.
+As we are interested mainly in the response of crops (corn, soy), only GOSAT measurements that cover at least $50\%$ any cropland-type surface were kept for the subsequent analysis, and we use the SIF retrievals at $755$ nm.
 
@@
 The bottom panel shows the anomalies, and the shaded area visualizes the respective minimum and maximum value of the given month to show the spread of the ROI-averaged SIF.
-We find that the variability in the six SIF time series stems mostly from the two different polarizations, rather than the calibration methodology.
-Months with less than $100$ measurements are dropped from both the visualization and the analysis, which affects only December $2012$ and January $2015$, months in which GOSAT was only partially operative due to instrumental issues.
+We find that the variability in the six SIF time series is mostly from the two different polarizations, rather than the calibration methodologies.
+Months with less than $100$ measurements are dropped from both the visualization and the analysis, which affects only December $2012$ and January $2015$ when GOSAT was only partially operative due to instrumental issues.
 
@@
 In the top panel, the green line represents the median of the six monthly-averaged SIF time series (two polarization states, three bias correction schemes), while the blue-dashed line represents the measurement count per month.
-The dotted lines in the bottom plot mark the $2\sigma$ and $3\sigma$ values of the anomalies.}
+The dotted lines in the bottom plot mark the $\pm 2\sigma$ and $\pm 3\sigma$ values of the anomalies, and the shaded area is bounded by the lowest and largest value of the six SIF time series.}
 \label{fig:sif_ts}
@@
 Given this relatively short period of seven years, only one month shows an anomalous value beyond $3\sigma$ (five months beyond $2\sigma$).
-We conclude that this short time period does not have a strong baseline, as most years have one ore more anomalous months.
-[REFERENCE WOLF LIU AND OTHERS AND POINT OUT THAT THEY USED A SIMPLE BASELINE] It is therefore imperative to look at every year and potential anomaly within the context of other climatological and agricultural drivers.
-In chronological order, they can be easily identified and related to known meteorological events.
+We conclude that this short time period does not have a clear baseline, and using a simple threshold based on the standard deviation, will result in either too few or too many anomalies.
+We point to two studies by \citet{sun2015drought} and \citet{wolf2016warm}, which both analyze drought events with respect to a similarly short baseline.
+\citet{sun2015drought} investigate the 2011 drought over Texas and the 2012 drought over most parts of the central US respectively, through SIF retrieved from GOME-2 in the 2007-2013 time period.
+
+[REFERENCE WOLF LIU AND OTHERS AND POINT OUT THAT THEY USED A SIMPLE BASELINE] It is therefore important to look at every year and potential anomaly within the context of other climatological and agricultural drivers.
+In chronological order, the major anomalies can be easily identified and related to known meteorological events.
 
@@
 The flooded areas, however, are visible as a positive anomaly in the GRACE data.
-While many farmers in the Mississippi River Valley were affected by planting delays due to levee breaches \citep{olson2012impacts} (maybe need better / more references to this), regions like Iowa, Nebraska and Kansas were not as severely impacted, hence the smaller anomaly.
+While many farmers in the Mississippi River Valley were affected by planting delays due to levee breaches \citep{olson2012impacts}, regions like Iowa, Nebraska and Kansas were not as severely impacted, hence the smaller anomaly.
 
@@
 In the spring months, high precipitation and cool temperatures delayed the planting process - corn seed planting is generally done on warm and dry days - as well as caused slow maturing of crops.
+The delayed planting is evident in the USDA surveys and displayed Figure~\ref{fig:corn_soy_planted_sif} (next section), which shows that the planting progress by calendar week 18 was the worst in the years $2013$ and $2014$.
 
@@
 %\label{fig:anomalies_2}
-%\end{figure}
-
-%\begin{figure}[htbp]
-%\centering
-%\includegraphics{../anomalies_755_abs_1_median.pdf}
-%\caption{default}
-%\label{fig:anomalies_1}
 %\end{figure}
@@
 
-We compare gross flux anomalies from CASA, as well as net flux anomalies obtained through the inversion of GOSAT XCO$_2$ measurements (see Section~\ref{sec:fluxes}) to the SIF anomalies.
-Figure~\ref{fig:anomalies_3} shows that the large drought event of 2012 is represented in both gross and net fluxes - several other anomalies (2010, 2011, 2015) are also well-represented in both flux data.
+We compare gross (GPP) and net flux (NPP) 
+anomalies from the Carnegie-Ames-Stanford-Approach (CASA) model, as well as net flux anomalies obtained through the inversion of GOSAT XCO$_2$ measurements (see Section~\ref{sec:fluxes}) to the SIF anomalies.
+Figure~\ref{fig:anomalies_3} shows that the large drought event of 2012 is represented in both gross and net fluxes - several other anomalies (2010, 2011, 2015) are also well-represented in both model fluxes, and the fluxes obtained through inversions.
+The surface fluxes anomalies here are also sampled at the GOSAT measurement locations.
+QUESTION: Is it legit to sample surface fluxes at GOSAT locations, or do I need the full ROI?
 
@@
 \includegraphics{../anomalies_755_abs_2_median.pdf}
-\caption{Flux anomalies [gC/m$^2$/yr] overlaid on top of SIF anomalies [W/m$^2$/sr/$\mu$m].}
+\caption{Flux anomalies [gC/m$^2$/yr] overlaid on top of SIF anomalies [mW/m$^2$/sr/nm].}
 \label{fig:anomalies_3}
@@
 Meteorological conditions are thus not the only factor in determining the vegetation onset and productivity of one given season.
-It was pointed out in Section~\ref{sec:SIF_TS} that for certain years, the rainfall amount in springtime have caused delays in the planting of crops.
+It was pointed out in Section~\ref{sec:SIF_TS} that for certain years, the springtime rainfall has caused delays in the planting of crops.
 To show that SIF indeed captures the delays in planting, we compare against the USDA crop progress reports \citep{USDA2010,USDA2011,USDA2012,USDA2013,USDA2014,USDA2015,USDA2016}.
@@
 We translate these weekly state-wide data for the whole ROI by multiplying with the total planted area for that given year and state in order to obtain an effective "planted area".
-We compare this number for every year against the integrated (or cumulative) SIF radiances (monthly ROI averages) from February onwards to June.
+We compare this number for every year against the integrated (or cumulative) SIF radiances (monthly ROI averages) from April onwards to June.
 
@@
 \centering
-\includegraphics{../corn_soy_planted_sif.pdf}
+\includegraphics{../corn_soy_planted_sif_18.pdf}
 \caption{Crop planting progress (1 acre $\approx 4047$ m$^2$) at week 18 as a function of time-integrated monthly SIF radiances from February to June.
 Uncertainty bars for SIF is the standard error on the 6 different SIF time series.
-Low values for the years $2013$ and $2014$ are the result of planting delays due to rainfall and cold temperatures (see Section \ref{sec:SIF_TS}).}
+Low values for the years $2013$ and $2014$ are the result of planting delays due to rainfall and cold temperatures (see Section \ref{sec:SIF_TS}).
+The values in the brackets within the regression equation (above plots) is the uncertainty of the fitted slope and offset.}
 \label{fig:corn_soy_planted_sif}
@@
 It shows that the time-integrated SIF radiances correspond very well to the crop planting progress of that given year at the first week of May (week 18).
-[TODO: If I change the months / weeks slightly - the result improves a bit; justification?]
+Week 18 was chosen as a reference point as it is generally in the first half of the planting season, which usually starts in early April, or week 14.
+\citet{grassini2011high} state the mean planting date (or sowing date) at day 117 of the year (last week of April) for the years 2005 to 2007 for their study in Nebraska.
+Between 2010 and 2016, planting progress has reached close to $100\%$ by week 23 (beginning of June) according to USDA surveys, and no planting has been done after week 26.
+Before week 17, the variability of planting is too high between nine states and the ROI-averaged SIF is therefore not representative of the Corn Belt as a whole.
+Table~\ref{tbl:planting_progress_table} shows the correlation coefficients of the relationships between SIF and planting progress (as in Figure~\ref{fig:corn_soy_planted_sif}) along with the coefficient of variation (COV) of the planting progress of the given week, averaged over the 7 years.
+
+\begin{table}[htp]
+\begin{center}
+\begin{tabular}{r|c|c|c|c}
+Week Nr. & COV Corn & COV Soybeans & Corn & Soybeans \\
+\hline
+16 & 1.04 & 1.37 & $r = 0.59$ & $r = 0.27$ \\
+17 & 0.80 & 1.06 & $r = 0.60$ & $r = 0.51$ \\
+18 & 0.48 & 0.96 & $r = 0.78$ & $r = 0.71$ \\
+19 & 0.31 & 0.61 & $r = 0.56$ & $r = 0.65$ \\
+20 & 0.18 & 0.45 & $r = 0.78$ & $r = 0.65$ \\
+%21 & 0.09 & 0.30 &            &            \\
+%22 & 0.05 & 0.21 &            &            \\
+\end{tabular}
+\end{center}
+\label{tbl:planting_progress_table}
+\caption{Relationship between cumulative SIF (Apr-Jun) and planting progress for different weeks of the year, each row representing the same analysis as in Figure~\ref{fig:corn_soy_planted_sif}.}
+\end{table}%
 
 The SIF radiances do not only reflect the crop status during the growing season.
-Also the total corn and soybean yield for the entire year has an apparent linear relationship with the integrated SIF radiances from June until October (harvest), as can be seen in Figure~\ref{fig:corn_soy_yield_sif}.
+Also the total corn and soybean yield for the entire year has an apparent linear relationship with the cumulative SIF radiances from July until October (harvest), as can be seen in Figure~\ref{fig:corn_soy_yield_sif}.
 The record-low yield due to the 2012 drought is highly apparent in the figure, also making it clear that a yield prognosis based on planting progress alone (Fig.~\ref{fig:corn_soy_planted_sif}) is not feasible.
@@
 \includegraphics{../corn_soy_yield_sif.pdf}
-\caption{Annual crop yield (1 bushel corn $\approx 25.4$ kg, 1 bushel soybean $\approx 27.2$ kg) from June to October as a function of the time-integrated monthly SIF radiances from June to October.
-The uncertainty bars for crop yield is the standard error of all nine states within the ROI, however that number is not taken into account for the linear regression.
-The value in the bracket within the regression equation is the uncertainty of the fitted slope and offset.}
+\caption{Annual crop yield (1 bushel corn $\approx 25.4$ kg, 1 bushel soybean $\approx 27.2$ kg) from June to October as a function of the time-integrated monthly SIF radiances from July to October.
+The uncertainty bars for crop yield is the standard error of all nine states within the ROI, however that number is not taken into account for the linear regression.}
 \label{fig:corn_soy_yield_sif}
@@
 
-The observed good relationship between SIF, and crop planting and crop yield is not particularly surprising, given the good correlation between SIF and NDVI/EVI time series anomalies ($r > 0.6$, not pictured).
-The predictive power of hyperspectral indices from remote sensing instruments in characterising crop yield has been demonstrated in the past, such as by \citet{Shanahan2001}, \citet{Prasad2006}, \citet{Beckerreshef2010} and \citet{Mkhabela2011}.
-Even in the case of the entire Corn Belt, NDVI/EVI remain better predictors than SIF for both planting ($r = 0.88$ / $r = 0.86$ for corn) and yield ($r = 0.98$ / $r = 0.96$ for corn).
-Similarly good predictors are leaf area index (LAI) and fractional vegetation cover (FVC) with $r = 0.92$ and $r = 0.90$ for corn planting, and $r = 0.98$ and $r = 0.98$ for corn yield.
-The better performance of NDVI/EVI as well as LAI and FVC most likely stem from the noisy nature of the SIF data (see Section \ref{sec:GOSAT_SIF}).
+The observed good relationship between cumulative SIF, and crop planting and crop yield is not particularly surprising, given the already moderate correlation between the SIF and NDVI/EVI time series anomalies ($r > 0.4$, see Appendix Figure~\ref{fig:anomalies_vi}).
+The predictive power of hyperspectral indices from remote sensing instruments in characterizing crop yield has been demonstrated in the past, such as by \citet{Shanahan2001}, \citet{Prasad2006}, \citet{Beckerreshef2010} and \citet{Mkhabela2011}.
+For the case of the Corn Belt, (monthly cumulative) NDVI/EVI are worse predictors than SIF for planting ($r = 0.59$ / $r = 0.56$ for corn) but slightly better predictors when looking at yield ($r = 0.91$ / $r = 0.87$ for corn).
+Similarly good predictors are leaf area index (LAI) and fractional vegetation cover (FVC) with $r = 0.90$ and $r = 0.86$ for corn yield, but are worse for corn planting progress ($r = 0.54$ / $r = 0.51$).
+%The better performance of NDVI/EVI as well as LAI and FVC most likely stem from the noisy nature of the SIF data (see Section \ref{sec:GOSAT_SIF}).
 Even at the scale of the ROI, monthly values of the ROI-averaged SIF can have an attached uncertainty of at least $\approx 20\%$ (estimated through sub-regional aggregation).
@@
 The first control is to look at the relationship between total planted area in the nine states against crop yield, where the planted area and yield values are separate for each crop.
-We see a positive correlation for soybeans ($r = 0.61$), whereas for corn, there is a surprising negative and weak correlation ($r = 0.27$).
+This is shown in Figure~\ref{fig:corn_soy_yield_TOTAL_PLANTED}.
+We see a positive correlation for soybeans ($r = 0.61$), whereas for corn, there is a surprising negative, weak ($r = 0.27$) and statistically insignificant correlation ($p=0.23$).
 This negative correlation for corn is solely due to the year 2012, removing that one data point reduces the correlation coefficient to $r = 0.00$, which is already hinted by the large p-value of $0.23$.
@@
 Here we use the same set of soundings that was pre-filtered beforehand, so only individual soundings are considered that cover more than $50\%$ of the crop type land cover type.
-The observed correlation at $r < 0.46$ is weaker than in Figure~\ref{fig:corn_soy_yield_VI_FRACTION} ($r > 0.75$), and neither relationship is statistically significant ($p > 0.15$).
+The observed correlations at $r < 0.36$ are weaker than in Figure~\ref{fig:corn_soy_yield_VI_FRACTION} ($r > 0.41$), but neither relationship is statistically significant ($p > 0.15$).
 
@@
 
+\appendix
+\section{Additional Plots}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{../anomalies_755_abs_1_median.pdf}
+\caption{SIF anomaly compared to the normalized differential vegetation index (NDVI), enhanced vegetation index (EVI), fractional vegetation cover (FVC) and leaf area index anomalies (LAI).
+Both FVC and LAI reproduce almost the same anomalies as SIF with the main difference being the strength of the positive 2010 anomaly, and LAI not showing any anomaly in 2014 at all.
+NDVI and EVI show a more extended positive anomaly for the 2011/2012 winter season.}
+\label{fig:anomalies_vi}
+\end{figure}
+
 \end{document}

### 2019-04-23 analysis.py

@@ -352,8 +352,8 @@ def ts_overview(plot_df, sif_list, aux_list,
         ax.legend(fontsize=7, loc='lower left', framealpha=1.0)
         # Standard deviation to spot where significant anomalies lie
         if hline is not None:
-            ax.hlines([-sif_data.median(axis=1).std(),
-                       sif_data.median(axis=1).std()],
+            ax.hlines([-3*sif_data.median(axis=1).std(),
+                       3*sif_data.median(axis=1).std()],
                       xmin=sif_data.index[0], xmax=sif_data.index[-1],
                       linestyle='dashed', color='g', lw=1.0)
 
@@ -502,6 +502,7 @@ aux_list = [#'gome2_sif',
     'myd11_lst_day',
     'sm_combined',
     #######
+    'myd13_ndvi',
     'myd13_evi',
     'fvc',
     'lai',
@@ -510,7 +511,7 @@ aux_list = [#'gome2_sif',
     ####
     #'myd13_ndvi',
     #####
-    'CASA_NEE', 'CASA_GEE', 'uoe-7.1b']
+    'CASA_GEE', 'CASA_NEE', 'uoe-7.1b']
 
 aux_labels = [#'GOME-2 SIF [mW/m$^2$/sr/nm]',
     'GRACE [cm]',
@@ -518,6 +519,7 @@ aux_labels = [#'GOME-2 SIF [mW/m$^2$/sr/nm]',
     'LST [K]',
     'Combined SM [m$^3$/m$^3$]',
     ####
+    'NDVI',
     'EVI',
     'FVC',
     'LAI',
@@ -526,12 +528,12 @@ aux_labels = [#'GOME-2 SIF [mW/m$^2$/sr/nm]',
     ####
     #'NDVI',
     ####
-    'CASA NPP [gC/m$^2$/yr]',
     'CASA GPP [gC/m$^2$/yr]',
+    'CASA NPP [gC/m$^2$/yr]',
     'UoE NPP [gC/m$^2$/yr]']
 
 sls = [slice(0,2), slice(3,6), slice(6,9), slice(9,10),  slice(11, 13)]
-sls = [slice(0,4), slice(4,7), slice(7,10)]
+sls = [slice(0,4), slice(4,8), slice(8,11)]
 
 for absrel, pol, window in itertools.product(
         ['abs', 'rel'], ['_P', '_S', ''], ['755', '772']):
[…]

### 2019-05-02 manuscript/manuscript.tex
Updates

@@
-\documentclass[preprint, a4paper, 10pt, times]{elsarticle}
+\documentclass[preprint, a4paper, 10pt, times, 5p]{elsarticle}
 
-\usepackage{lineno, hyperref}
+\usepackage{hyperref}
 
+\usepackage[switch]{lineno}
 \modulolinenumbers[5]
@@
 %% Harvard
-%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
+\bibliographystyle{model2-names.bst}\biboptions{authoryear}
 
@@
 %% APA style
-\bibliographystyle{model5-names}\biboptions{authoryear}
+%\bibliographystyle{model5-names}\biboptions{authoryear}
 
@@
 
-\title{A Multi-Satellite Investigation of the US Corn Belt in the Period 2010-2016 with a Focus on Solar-Induced Fluorescence}
+\title{A Multi-Satellite Investigation of the US Corn Belt in the Period 2010-2016 with a Focus on Solar-Induced Fluorescence - PAUL SAYS I NEED SEXIER TITLE}
 
@@
 This so-called \textit{physically-based} retrieval is derived from the Fraunhofer line discrimination method, first described in \citet{plascyk_fraunhofer_1975}.
-Briefly summarized, the method relies on the fact that any additive radiation originating from the surface will reduce the fractional depth of Fraunhofer lines in the top-of-atmosphere (TOA) spectrum.
+Briefly summarized, the method relies on the fact that any additive radiation originating from the surface will reduce the fractional depth of Fraunhofer lines in the top of atmosphere (TOA) spectrum.
 It is therefore possible to decouple reflectance from the additive fluorescence contribution to the total TOA radiance.
-TANSO-FTS records radiances in the near-visible to shortwave infrared wavelength range in two linear polarization states: P - parallel, and S - perpendicular to the plane of incidence (?
-or is it principal plane?).
+TANSO-FTS records radiances in the near-visible to shortwave infrared wavelength range in two linear polarization states: P - parallel, and S - perpendicular to the sensor plane, spanned between the radial Earth-spacecraft vector, the spacecraft velocity vector, and the vector between spacecraft yaw and spacecraft velocity.
 
@@
 A crucial step in the SIF retrieval process is the bias correction.
-Small non-linearities in the analogue-to-digital conversion of the TANSO-FTS interferograms lead to the same fractional reduction of Fraunhofer lines as any SIF signal would do and thus result in unphysical SIF values.
+Small non-linearities in the analog-to-digital conversion of the TANSO-FTS interferograms lead to the same fractional reduction of Fraunhofer lines as any SIF signal would do and thus result in unphysical SIF values.
 In order to rid the measurements of these instrument artefacts, the retrieved SIF values need to be corrected.
@@
 
-We produce calibration curves via the relationship between retrieved offset ($z_0$) and the mean radiance in the entire first GOSAT band.
-Ideally, this curve would be flat and centered around zero, however the instrumental artefacts lead to a somewhat complicated shape, as shown in Figure XX [should I put a figure here?
-or is this too technical already..].
+We produce calibration curves via the relationship between retrieved offset and the mean radiance in the entire first GOSAT band.
+Ideally, this curve would be flat and centered around zero, however the instrumental artefacts lead to a somewhat complicated shape, as shown in Figure~\ref{fig:calibration_curves}.
 This instrumental bias varies over time and requires a time-dependent correction.
@@
 GOSAT/TANSO-FTS was designed to measure atmospheric quantities, and thus differs from imaging-type measurement concepts (e.g.~MODIS) that are tailored to the measurement of surface quantities.
-The high-resolution spectrometer points at one location at a time with an instantaneous field of view (IFOV) of ZYX$^\circ$, which corresponds roughly to a circular footprint with $10.5\:\mathrm{km}$ diameter at nadir viewing geometry.
+The high-resolution spectrometer points at one location at a time with an instantaneous field of view (IFOV) of $15.8$ mrad, which corresponds roughly to a circular footprint with $10.5\:\mathrm{km}$ diameter at nadir viewing geometry.
 As a consequence, it is necessary to consider the specific sampling pattern for the data sets in the analysis in order to avoid sampling bias (see Section~\ref{sec:sampling_bias}).
@@
 \item MODIS/Aqua MYD11C2 V006 Land Surface Temperature ($0.05^\circ$ resolution, $2010-2016$) \citep{MYD11C2}
-\item SPOT/VEGETATION Leaf Area Index V2.0.1 ($1\:\mathrm{km}$ resolution, $2010-2016$)
-\item SPOT/VEGETATION Fractional Vegetation Cover V2.0.1 ($1\:\mathrm{km}$ resolution, $2009-2016$)
-\item TRMM (3B43, multi-satellite) precipitation ($0.25^\circ$ resolution, $2010-2016$)
+\item SPOT/VGT Leaf Area Index V2.0.1 ($1\:\mathrm{km}$ resolution, $2010-2016$) \citep{maisongrande2004vegetation}
+\item SPOT/VGT Fractional Vegetation Cover V2.0.1 ($1\:\mathrm{km}$ resolution, $2009-2016$) \citep{maisongrande2004vegetation}
+\item TRMM/TPMA (3B43, multi-satellite) precipitation ($0.25^\circ$ resolution, $2010-2016$) \citep{huffman2007trmm}
 \end{itemize}
 
-For the MODIS/Aqua, ESA CCI Land Cover and SPOT/VEGETATION datasets, the scene-specific footprint is fully taken into account.
+For collocation of the EVI/NDVI, ESA CCI Land Cover and FVC/LAI datasets, the scene-specific GOSAT footprint is fully taken into account.
 Only those pixels are aggregated to the scene-specific value, whose pixel area overlaps by at least $50\%$ with the GOSAT footprint.
-Soil moisture and TRMM precipitation data, however, are of lower resolution where sub-pixel aggregation is not required.
-For TRMM, the grid box is taken in which the GOSAT footprint lies, and for the soil moisture data (which is supplied on grid points rather than grid boxes [DOUBLE CHECK!!]), bi-linear interpolation of the closest four grid points is used.
+Soil moisture and TRMM/TPMA precipitation data, however, are of lower resolution where sub-pixel aggregation is not required.
+For TRMM/TPMA, the grid box is taken in which the GOSAT footprint lies, and for the soil moisture data (which is supplied on grid points rather than grid boxes), bi-linear interpolation of the closest four grid points is used.
 
-In the time dimension, linear interpolation is used for all data sets except for land cover data (annual) and TRMM (monthly).
+In the time dimension, linear interpolation is used for all data sets except for land cover data (annual) and TRMM/TPMA precipitation data (monthly).
 
@@
 
-\subsection{Agricultural Statistics from USDA}
+\subsection{Agricultural Statistics from the United States Department for Agriculture}
 \label{sec:usda}
+To help interpret the various SIF anomalies in Section~\ref{sec:SIF_TS}, we use the crop summary reports published by the United States Department for Agriculture (USDA).
+These reports are released annually and contain, amongst other items, overview statistics on crop planting acreage and harvest yield for a given year.
+They also provide a succinct overview of the climate conditions from planting to harvest and highlight meteorological events and their impacts on agriculture.
+The second USDA resource used here is the USDA crop survey database (accessed online through https://www.nass.usda.gov/), which collects farmer survey data that allows tracking overall planting progress on a weekly basis at varying levels of spatial aggregation (we used per-state).
 
@@
 \centering
-\includegraphics{../coverage_map.png}
+\includegraphics[width=\linewidth]{../coverage_map.png}
 \caption{Land cover classes (left) and GOSAT sampling density (right) shown for the region of interest ($104$W - $87.5$W, $37$N - $49$N).
@@
 \includegraphics{../lc_coverage.pdf}
-\caption{Comparison of overall land cover coverage between the entire ROI and GOSAT sampling.}
+\caption{A comparison of overall land cover coverage between the entire ROI and GOSAT sampling. This confirms that the sparse GOSAT sampling pattern well-represents the surface types within the ROI.}
 \label{fig:lc_coverage}
@@
 
-Not surprising, more than $75\%$ of surfaces belong to either rainfed cropland or grassland types.
+More than $75\%$ of surfaces belong to either rainfed cropland or grassland types.
 The third most common surface type (deciduous tree cover) is mainly due to Ozark National Forest in Missouri, Superior National Forest as well as forests in northern Wisconsin.
-For the total period, GOSAT is well representing the overall composition of land cover classes of the region of interest.
+For the total period, GOSAT is well-representing the overall composition of land cover classes of the region of interest.
 The largest differences are seen for flooded tree cover, where GOSAT is slightly over-representing ($+1.7\%$), and grassland, where GOSAT is under-representing ($-3.3\%$).
@@
 It is also important to note that while Figures~\ref{fig:lc_coverage} and \ref{fig:lc_diff_monthly} confirm that the LC classes are more or less well-represented, vegetation responses can vary geographically over the Corn Belt, even though they might share the same LC classification.
+Geographically varying differences in planting dates can lead to crops maturing at different times and thus dilute the ROI-averaged vegetation signals picked up via remote sensing.
 
-As we are interested mainly in the response of crops (corn, soy), only GOSAT measurements that cover at least $50\%$ any cropland-type surface were kept for the subsequent analysis, and we use the SIF retrievals at $755$ nm.
+As we are interested mainly in the response of crops (corn, soy), only GOSAT measurements that cover at least $50\%$ of any cropland-type surface were kept for the subsequent analysis, and we use the SIF retrievals at $755$ nm.
 
@@
 
-\subsection{SIF time series}
+\subsection{SIF time series and anomalies between 2010 and 2016}
 \label{sec:SIF_TS}
@@
 \centering
-\includegraphics{../SIF_overview.pdf}
+\includegraphics[width=\linewidth]{../SIF_overview.pdf}
 \caption{The SIF time series (top panel) and corresponding anomaly plot (bottom panel).
@@
 We point to two studies by \citet{sun2015drought} and \citet{wolf2016warm}, which both analyze drought events with respect to a similarly short baseline.
-\citet{sun2015drought} investigate the 2011 drought over Texas and the 2012 drought over most parts of the central US respectively, through SIF retrieved from GOME-2 in the 2007-2013 time period.
-
-[REFERENCE WOLF LIU AND OTHERS AND POINT OUT THAT THEY USED A SIMPLE BASELINE] It is therefore important to look at every year and potential anomaly within the context of other climatological and agricultural drivers.
+\citet{wolf2016warm} establish flux anomalies from three eddy covariance towers based on a 2008-2010 baseline,  \citet{sun2015drought} investigate the 2011 drought over Texas and the 2012 drought over most parts of the central US respectively, through SIF retrieved from GOME-2 in the 2007-2013 time period.
+While the 2011 and 2012 anomalies are both apparent in the given time period, we argue that their magnitude might be wrongly assessed if not compared against the other anomalies.
+It is therefore important to look at every year and potential anomaly within the context of other climatological and agricultural drivers.
 In chronological order, the major anomalies can be easily identified and related to known meteorological events.
 
-Starting in $2010$, we see the effects of the rapid El Ni\~no-La Ni\~na transition, which brought excessive rain to the Corn Belt in the summer months (Fig.~\ref{fig:anomalies_0} second row) and drove plant growth \citep{USDA2010}.
+Starting in $2010$, we see the effects of the rapid El Ni\~no-La Ni\~na transition, which brought excessive rain to the Corn Belt in the summer months and drove plant growth \citep{USDA2010}.
+This is confirmed through the TRMM/TPMA rainfall anomaly that can be seen in Figure~\ref{fig:anomalies_0}, second row.
 
@@
 The flooded areas, however, are visible as a positive anomaly in the GRACE data.
-While many farmers in the Mississippi River Valley were affected by planting delays due to levee breaches \citep{olson2012impacts}, regions like Iowa, Nebraska and Kansas were not as severely impacted, hence the smaller anomaly.
+While many farmers in the Mississippi River Valley were affected by planting delays due to levee breaches \citep{olson2012impacts}, productive states like Iowa, Nebraska and Kansas were not as severely impacted, hence the lack of a pronounced anomaly \citep{USDA2011}.
 
@@
 In short, a warm winter and warm spring (see LST anomalies in Fig.~\ref{fig:anomalies_0} third row) caused early and fast vegetation growth.
-In the following summer, however, anomalously low precipitation (Fig.~\ref{fig:anomalies_0} second row) was responsible for drought conditions.
+In the following summer, however, anomalously low precipitation (Fig.~\ref{fig:anomalies_0}, second row) was responsible for drought conditions.
 As a consequence of the early spring onset due to warm temperatures, the plants used up soil water reserves quicker and depleted the soil of moisture, thus exacerbating the drought even further.
@@
 For these two years, the anomalies have similar causes.
-In the spring months, high precipitation and cool temperatures delayed the planting process - corn seed planting is generally done on warm and dry days - as well as caused slow maturing of crops.
-The delayed planting is evident in the USDA surveys and displayed Figure~\ref{fig:corn_soy_planted_sif} (next section), which shows that the planting progress by calendar week 18 was the worst in the years $2013$ and $2014$.
+In the spring months, high precipitation and cool temperatures delayed the planting process - corn seed planting is generally done on warm and dry days \citep{kucharik2008contribution,choi2017climatic} - as well as caused slow maturing of crops.
+The delayed planting is evident in the USDA surveys and displayed in Figure~\ref{fig:corn_soy_planted_sif} (next section), which shows that the planting progress by calendar week 18 was lowest in the years $2013$ and $2014$ \citep{USDA2013,USDA2014}.
 
@@
 $2016$ proved to be an even better year for crop production than $2015$, and this is reflected in the SIF anomaly.
-After an intense El Ni\~no in $2015$, the quick transition to a weak La Ni\~na, and a wet summer has provided ideal conditions for crops.
+After an intense El Ni\~no in $2015$, the quick transition to a weak La Ni\~na, and a wet summer has provided ideal conditions for crops \citep{USDA2015,USDA2016}.
 
 A short summary is given in Table~\ref{tbl:anomaly_table}.
+The USDA crop summary reports highlight the fact that almost every year between 2010 and 2016 had one or more meteorological events occur which impacted the Corn Belt agriculture.
 
@@
 \centering
-\includegraphics{../anomalies_755_abs_0_median.pdf}
-\caption{Anomalies of GRACE water equivalent thickness (cm), precipitation, land surface temperature and soil moisture (all in blue), along with SIF anomalies (dashed, green).}
+\includegraphics[width=\linewidth]{../anomalies_755_abs_0_median.pdf}
+\caption{Anomalies of GRACE water equivalent thickness (cm), precipitation, land surface temperature and soil moisture (all in blue), along with SIF anomalies (dashed, green).
+The ordinate axes ticks on the left hand side refer to the non-SIF anomalies (GRACE, precipitation, LST, soil moisture).
+SIF anomalies are plotted for visual comparison, and tick labels have been omitted for better legibility.
+The GRACE time series has several gaps, which is mainly due to aging batteries on the GRACE satellite.}
 \label{fig:anomalies_0}
@@
              & & high precipitation during summer \\
-$2011$ & $-$   & Snow melt caused flooding, delaying planting \\
-             & & in some areas of the Corn Belt (NM, SD, ND, WI) \\
+$2011$ & $-$   & Snow melt caused flooding, delaying \\
+             & & planting in MN, SD, ND, and WI \\
 $2012$ & $+/-$ & Warm spring induced early onset, \\
@@
              & & despite large rainfall due to El Ni\~no \\
-$2016$ & $+$ & Weak La Ni\~na/wet summer for good conditions \\
+$2016$ & $+$   & Weak La Ni\~na/wet summer for \\
+             & & good conditions \\
 \end{tabular}
@@
 SIF is intrinsically linked to primary production (GPP) as it is a by-product of the photosynthetic process that ultimately leads to carbon fixation.
-As such, the relationship between SIF and GPP has been explored early on when global-scale retrievals of SIF were performed \citep{Frankenberg2011,Guanter2012}.
+As such, the relationship between SIF and GPP has been explored early on when global-scale retrievals of SIF were performed \citep{Joiner2011,Frankenberg2011,Guanter2012}.
 The SIF-GPP relationship has been described as linear when averaged on regional scale and with time, with a potential dependence on biome.
@@
 
-We compare gross (GPP) and net flux (NPP) 
-anomalies from the Carnegie-Ames-Stanford-Approach (CASA) model, as well as net flux anomalies obtained through the inversion of GOSAT XCO$_2$ measurements (see Section~\ref{sec:fluxes}) to the SIF anomalies.
+We compare gross (GPP) and net flux (NPP) anomalies from the Carnegie-Ames-Stanford-Approach (CASA) model \citep{potter1993terrestrial}, as well as net flux anomalies obtained through a global inversion of GOSAT XCO$_2$ total column measurements (see Section~\ref{sec:fluxes}) to the SIF anomalies.
 Figure~\ref{fig:anomalies_3} shows that the large drought event of 2012 is represented in both gross and net fluxes - several other anomalies (2010, 2011, 2015) are also well-represented in both model fluxes, and the fluxes obtained through inversions.
 The surface fluxes anomalies here are also sampled at the GOSAT measurement locations.
-QUESTION: Is it legit to sample surface fluxes at GOSAT locations, or do I need the full ROI?
 
-\begin{figure}[htbp]
+\begin{figure}[htb!]
 \centering
-\includegraphics{../anomalies_755_abs_2_median.pdf}
-\caption{Flux anomalies [gC/m$^2$/yr] overlaid on top of SIF anomalies [mW/m$^2$/sr/nm].}
+\includegraphics[width=\linewidth]{../anomalies_755_abs_2_median.pdf}
+\caption{Flux anomalies [gC/m$^2$/yr] overlaid on top of SIF anomalies [mW/m$^2$/sr/nm]. CASA GPP is used as a prior for the flux inversion scheme.}
 \label{fig:anomalies_3}
 \end{figure}
+
+While we did not perform high-resolution flux inversions as done by \citet{lauvaux2012constraining}, we do see that the posterior net fluxes, integrated over the growing period Apr-Jul, agree better with the cumulative SIF when compared to CASA net fluxes, as shown in Figure~\ref{fig:SIF_flux_cumulative}.
+The CASA GPP, however, compares even better ($r = 0.92$).
+Again, this is most likely due to CASA GPP being constrained by NDVI, and a similar analysis between cumulative SIF and cumulative NDVI yielding moderate agreement already ($r = 0.57$, not shown).
+
+\begin{figure}[htb!]
+\centering
+\includegraphics[width=\linewidth]{../SIF_flux_cumulative_CASA_NEE.pdf}
+\caption{yadda yadda}
+\label{fig:SIF_flux_cumulative}
+\end{figure}
+
+SIF is generally thought to be a proxy for gross carbon uptake, rather than net flux, so the good agreement between integrated fluxes and SIF ($r = 0.70$) might seem surprising.
+The difference between total carbon uptake and net fluxes are usually summarized in the respiration term which (over land surfaces) comprises plant respiration, soil respiration and litter decomposition.
+From a flux inversion point of view, respiration and its components can not be easily disentangled from the net fluxes.
+\citet{byrne2018evaluating} have published efforts using models and SIF to decompose posterior (net) fluxes from respiration.
+Given that respiration roughly follows the trend of total uptake, and that we observe a large spatially-averaged and time-integrated composite signal, the agreement between posterior fluxes from the inversion and GOSAT SIF is reasonable.
+
+\textit{I CAN NOT MAKE THIS WORK AT ALL - ANY IDEAS? I DON'T THINK WE HAVE THE TIME/EFFORT TO VALIDATE THE FLUXES LIKE IN THE LAUVAUX/SCHUH PAPER, SO WHAT ARE WE GOING TO DO HERE?}
 
@@
 It was pointed out in Section~\ref{sec:SIF_TS} that for certain years, the springtime rainfall has caused delays in the planting of crops.
-To show that SIF indeed captures the delays in planting, we compare against the USDA crop progress reports \citep{USDA2010,USDA2011,USDA2012,USDA2013,USDA2014,USDA2015,USDA2016}.
+To show that SIF indeed captures the delays in planting, we compare against the USDA/NASS survey data.
 In these reports, the percentage of acreage planted is recorded based on farmer surveys.
@@
 \centering
-\includegraphics{../corn_soy_planted_sif_18.pdf}
+\includegraphics[width=\linewidth]{../corn_soy_planted_sif_18.pdf}
 \caption{Crop planting progress (1 acre $\approx 4047$ m$^2$) at week 18 as a function of time-integrated monthly SIF radiances from February to June.
@@
 The result for both corn and soybeans is shown in Figure~\ref{fig:corn_soy_planted_sif}.
-It shows that the time-integrated SIF radiances correspond very well to the crop planting progress of that given year at the first week of May (week 18).
+It shows that the time-integrated SIF radiances correspond well to the crop planting progress of that given year at the first week of May (week 18).
 Week 18 was chosen as a reference point as it is generally in the first half of the planting season, which usually starts in early April, or week 14.
@@
 Before week 17, the variability of planting is too high between nine states and the ROI-averaged SIF is therefore not representative of the Corn Belt as a whole.
-Table~\ref{tbl:planting_progress_table} shows the correlation coefficients of the relationships between SIF and planting progress (as in Figure~\ref{fig:corn_soy_planted_sif}) along with the coefficient of variation (COV) of the planting progress of the given week, averaged over the 7 years.
+Table~\ref{tbl:planting_progress_table} shows the correlation coefficients of the relationships between SIF and planting progress (as in Figure~\ref{fig:corn_soy_planted_sif}) along with the coefficient of variation (COV) of the planting progress of the given week for all states, averaged over the 7 years.
+A higher value indicates larger variation in planting progress between the nine states.
 
@@
 \begin{tabular}{r|c|c|c|c}
-Week Nr. & COV Corn & COV Soybeans & Corn & Soybeans \\
+Week Nr. & COV Corn & COV Soy & Corn & Soy \\
 \hline
-16 & 1.04 & 1.37 & $r = 0.59$ & $r = 0.27$ \\
-17 & 0.80 & 1.06 & $r = 0.60$ & $r = 0.51$ \\
-18 & 0.48 & 0.96 & $r = 0.78$ & $r = 0.71$ \\
-19 & 0.31 & 0.61 & $r = 0.56$ & $r = 0.65$ \\
-20 & 0.18 & 0.45 & $r = 0.78$ & $r = 0.65$ \\
+16 & 1.04 & 1.37 & $r = 0.77$ & $r = 0.23$ \\
+17 & 0.80 & 1.06 & $r = 0.77$ & $r = 0.66$ \\
+18 & 0.48 & 0.97 & $r = 0.92$ & $r = 0.91$ \\
+19 & 0.31 & 0.62 & $r = 0.70$ & $r = 0.79$ \\
+20 & 0.18 & 0.45 & $r = 0.69$ & $r = 0.66$ \\
 %21 & 0.09 & 0.30 &            &            \\
@@
 \label{tbl:planting_progress_table}
-\caption{Relationship between cumulative SIF (Apr-Jun) and planting progress for different weeks of the year, each row representing the same analysis as in Figure~\ref{fig:corn_soy_planted_sif}.}
+\caption{Relationship between cumulative SIF (Apr-Jun) and planting progress for different weeks of the year, each row representing the same analysis as in Figure~\ref{fig:corn_soy_planted_sif}.
+Soybean planting generally does not start until week 17.}
 \end{table}%
@@
 Also the total corn and soybean yield for the entire year has an apparent linear relationship with the cumulative SIF radiances from July until October (harvest), as can be seen in Figure~\ref{fig:corn_soy_yield_sif}.
-The record-low yield due to the 2012 drought is highly apparent in the figure, also making it clear that a yield prognosis based on planting progress alone (Fig.~\ref{fig:corn_soy_planted_sif}) is not feasible.
+The record-low yield due to the 2012 drought is also highly apparent in the figure.
+As the SIF integration time goes past the reference planting date, we assume that the cumulative SIF tracks the planting onset by proxy through the development of the crops in their first three months.
+
+This type of analysis has been published before, recently in a study by \citet{glennie2018midwest}, in which they use a long-term (1982 - 2014) NDVI record from the Advanced Very High Resolution Radiometer (AVHRR) instrument and compare them to yield data.
+Due to the high spatial resolution of the AVHRR instrument (8 km) and coverage (2500 km swath width), their cumulative NDVI-to-yield relationship could be established year-to-year, comparing annual yields for individual counties in the Corn Belt.
+They find moderately strong correlations ($r > 0.58$) which varies for every year.
+As  \citet{glennie2018midwest} have done, we have also detrended the crop yields using a linear fit through the mean yields from 1955 onwards, although the impact on the results is small, mostly due to the short time period.
 
@@
 \centering
-\includegraphics{../corn_soy_yield_sif.pdf}
+\includegraphics[width=\linewidth]{../corn_soy_yield_sif.pdf}
 \caption{Annual crop yield (1 bushel corn $\approx 25.4$ kg, 1 bushel soybean $\approx 27.2$ kg) from June to October as a function of the time-integrated monthly SIF radiances from July to October.
-The uncertainty bars for crop yield is the standard error of all nine states within the ROI, however that number is not taken into account for the linear regression.}
+The uncertainty bars for crop yield represent the standard deviation for the values of all nine states within the ROI.
+The color/symbol coding is the same as in Figure~\ref{fig:corn_soy_planted_sif}.}
 \label{fig:corn_soy_yield_sif}
@@
 The observed good relationship between cumulative SIF, and crop planting and crop yield is not particularly surprising, given the already moderate correlation between the SIF and NDVI/EVI time series anomalies ($r > 0.4$, see Appendix Figure~\ref{fig:anomalies_vi}).
-The predictive power of hyperspectral indices from remote sensing instruments in characterizing crop yield has been demonstrated in the past, such as by \citet{Shanahan2001}, \citet{Prasad2006}, \citet{Beckerreshef2010} and \citet{Mkhabela2011}.
-For the case of the Corn Belt, (monthly cumulative) NDVI/EVI are worse predictors than SIF for planting ($r = 0.59$ / $r = 0.56$ for corn) but slightly better predictors when looking at yield ($r = 0.91$ / $r = 0.87$ for corn).
-Similarly good predictors are leaf area index (LAI) and fractional vegetation cover (FVC) with $r = 0.90$ and $r = 0.86$ for corn yield, but are worse for corn planting progress ($r = 0.54$ / $r = 0.51$).
+The predictive power of hyperspectral indices from remote sensing instruments in characterizing and predicting crop yield has been demonstrated in the past, such as by \citet{Shanahan2001}, \citet{Prasad2006}, \citet{Beckerreshef2010}, \citet{Mkhabela2011}, \citet{sakamoto2014near} and many more.
+For the case of the Corn Belt, (monthly cumulative) NDVI/EVI are slightly worse predictors than SIF for planting ($r = 0.72$ / $r = 0.69$ for corn) similarly good predictors when looking at yield ($r = 0.90$ / $r = 0.88$ for corn).
+Similarly good predictors are leaf area index (LAI) and fractional vegetation cover (FVC) with $r = 0.91$ and $r = 0.87$ for corn yield and corn planting progress ($r = 0.84$ / $r = 0.77$).
 %The better performance of NDVI/EVI as well as LAI and FVC most likely stem from the noisy nature of the SIF data (see Section \ref{sec:GOSAT_SIF}).
@@
 A potential weakness regarding the relationship between SIF and crop yields is the following.
-We cannot simply deduce from the SIF measurements alone, whether GOSAT is observing stronger SIF due to the photosynthetic response of crops, or whether GOSAT is merely seeing larger amounts of vegetated area.
-To exclude this possibility, we construct three control time series to compare against the results seen in Figure~\ref{fig:corn_soy_yield_sif}.
+We cannot simply deduce from the SIF measurements alone, whether GOSAT is observing stronger SIF due to the photosynthetic response of crops, or if the footprints are merely seeing larger amounts of vegetated area.
+We can easily establish that the retrieved surface reflectivity (Lambertian albedo) is not contributing to the observed relationships, as the SIF and albedo anomalies are not correlated ($r < 0.11$).
+To further exclude the possibility of GOSAT SIF measuring only the change in vegetated area, we construct three control time series to compare against the results seen in Figure~\ref{fig:corn_soy_yield_sif}.
 
-The first control is to look at the relationship between total planted area in the nine states against crop yield, where the planted area and yield values are separate for each crop.
+The first control aims at the relationship between total planted area in the nine states against crop yield, where the planted area and yield values are separate for corn and soybeans.
 This is shown in Figure~\ref{fig:corn_soy_yield_TOTAL_PLANTED}.
-We see a positive correlation for soybeans ($r = 0.61$), whereas for corn, there is a surprising negative, weak ($r = 0.27$) and statistically insignificant correlation ($p=0.23$).
+We see a positive correlation for soybeans ($r = 0.61$), whereas for corn, there is a surprising negative, weak correlation  ($r = 0.27$) with low statistical significance ($p = 0.23$).
 This negative correlation for corn is solely due to the year 2012, removing that one data point reduces the correlation coefficient to $r = 0.00$, which is already hinted by the large p-value of $0.23$.
@@
 The USDA projects soybeans to reach similar levels to corn in terms of amount of planted acres in the near future \citep{USDA-prognosis}.
-We cannot distinguish whether a specific GOSAT footprint covered a soy field or a corn field (or any other crop) at the time of measurement.
+With the used auxiliary data, we cannot distinguish whether a specific GOSAT footprint covered a soy field or a corn field (or any other crop) at the time of measurement.
 Hence we can not completely reject the possibility that the SIF signal we see in Figure~\ref{fig:corn_soy_yield_sif} is due to mainly covering soybean fields.
-Since most farmers in the Corn Belt practice individual crop rotation between corn and soybeans \citep{suyker2012gross}, it is most likely that we are sampling a mix between corn, soybeans, and to a lesser extent, wheat.
+\textbf{The USDA crop data layer would provide this information at high resolution.} Since most farmers in the Corn Belt practice individual crop rotation between corn and soybeans \citep{suyker2012gross}, it is most likely that we are sampling a mix between corn, soybeans, and to a lesser extent, wheat, and that the relative contribution of each crop does not vary by large amounts over the years.
 We therefore assume that the SIF-yield relationship is not driven due to sampling that is heavily weighted towards soybean fields.
@@
 \centering
-\includegraphics{../corn_soy_yield_TOTAL_PLANTED.pdf}
+\includegraphics[width=\linewidth]{../corn_soy_yield_TOTAL_PLANTED.pdf}
 \caption{Crop yield versus the total planted area in that year, with planted area vales for the specific crop.}
@@
 Both correlation coefficients are statistically not significant with $p > 0.1$, mainly due to the fact that the NDVI fraction only changes by about $1\%$.
-Compared to Figure~\ref{fig:corn_soy_yield_TOTAL_PLANTED}, we cannot distinguish whether a pixel belongs to a corn or soybean field, and hence cannot split the NDVI fraction into corn and soy components.
+As opposed to Figure~\ref{fig:corn_soy_yield_TOTAL_PLANTED}, we cannot distinguish whether a pixel belongs to a corn or soybean field, and hence cannot split the NDVI fraction into corn and soy components.
 
@@
 \centering
-\includegraphics{../corn_soy_yield_VI_FRACTION.pdf}
+\includegraphics[width=\linewidth]{../corn_soy_yield_VI_FRACTION.pdf}
 \caption{Crop yield vs the fraction of valid NDVI pixels $> 0.3$.
@@
 \centering
-\includegraphics{../ndvi_crop/2012_VI_11_maximum.pdf}
+\includegraphics[width=\linewidth]{../ndvi_crop/2012_VI_11_maximum.pdf}
 \caption{THIS IS A DEBUG PLOT - DELETE ME.
@@
 Here we use the same set of soundings that was pre-filtered beforehand, so only individual soundings are considered that cover more than $50\%$ of the crop type land cover type.
-The observed correlations at $r < 0.36$ are weaker than in Figure~\ref{fig:corn_soy_yield_VI_FRACTION} ($r > 0.41$), but neither relationship is statistically significant ($p > 0.15$).
+The observed correlations at $r < 0.36$ are weaker than in Figure~\ref{fig:corn_soy_yield_VI_FRACTION} ($r > 0.41$), but neither relationship seems statistically significant ($p > 0.15$).
 
@@
 \centering
-\includegraphics{../corn_soy_yield_LC_FRACTION.pdf}
+\includegraphics[width=\linewidth]{../corn_soy_yield_LC_FRACTION.pdf}
 \caption{Crop yield vs the total fraction LC crop type surface seen in a given year.}
@@
 We thus conclude that GOSAT SIF (and vegetation indices) does not merely track whether a surface was vegetated, but can also provide information on the vegetation density and yield through the intensity of the signal.
+We treat these results cautiously, however, as the results shown in Figures~\ref{fig:corn_soy_planted_sif} and \ref{fig:corn_soy_yield_sif}.
 
 \section{Conclusions}
+We have presented a study of the US Corn Belt over the period of 7 years (2010-2016) that focuses on inter-annual variability and puts apparent anomalies into the context of agriculture.
+Several satellite-based data products were used to construct a coherent picture of the vegetation responses, which were mainly interpreted through GOSAT-based SIF with the help of USDA crop summary reports, which proved an invaluable resource.
+While we remain careful about claiming SIF to be superior compared to the more traditional reflectance-based vegetation indices, our work hints towards that being the case for this particular region.
+We were able to make a thorough comparison only because sampling was taken into account very carefully, ensuring that time series anomalies were calculated by considering the spatial extent of GOSAT footprints.
+Due to exactly collocating other satellite-based datasets, we are able to keep sampling bias to a minimum when comparing GOSAT SIF to other surface-type and atmospheric variables.
+While data sparsity is an issue, we are hopeful that in the near future, space-based SIF measurements can play a supporting role in crop monitoring and yield prediction, along with the traditional reflectance-based vegetation indices.
+
+The biggest challenge of this type of analysis remains the particular sampling pattern of GOSAT, which is non-uniform as well as low in the total number of measurements in a given time period.
+Due to the low number of measurements, it is both very difficult to analyze regions much smaller Corn Belt, as well as using smaller time intervals than a month.
+Newer space-based instruments, such as OCO-2 and TROPOMI, however, are capable of measuring SIF at a much higher spatial resolution \citep{sun2018overview,kohler2018global}.
+Especially TROPOMI has the advantage of being a wide-swath instrument, which provides near-global coverage on a daily basis.
+The ESA Earth Explorer Mission FLEX \citep{drusch2017fluorescence} is dedicated to SIF and will launch in 2023.
+Despite being designed for smaller swath (150 km), its 300m resolution FLORIS instrument will provide an opportunity to observe SIF on the scale of crop fields.
+%In the coming years, we expect to see more work on crop monitoring and yield prediction being published using SIF from these new space-based instruments.
 
@@
 \centering
-\includegraphics{../anomalies_755_abs_1_median.pdf}
+\includegraphics[width=\linewidth]{../2012_curves_lowess2.pdf}
+\caption{GOSAT SIF calibration curves for P and S polarized radiances, based on measurements from the year 2012.
+$z_0$ is the raw, uncorrected SIF, here in units of percentage of the mean radiance in the O$_2$ A-band (band 1).
+The high- and medium-gain measurements differ significantly in terms of their radiance-dependence.}
+\label{fig:calibration_curves}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=\linewidth]{../anomalies_755_abs_1_median.pdf}
 \caption{SIF anomaly compared to the normalized differential vegetation index (NDVI), enhanced vegetation index (EVI), fractional vegetation cover (FVC) and leaf area index anomalies (LAI).
 Both FVC and LAI reproduce almost the same anomalies as SIF with the main difference being the strength of the positive 2010 anomaly, and LAI not showing any anomaly in 2014 at all.
-NDVI and EVI show a more extended positive anomaly for the 2011/2012 winter season.}
+NDVI and EVI show a more extended positive anomaly for the 2011/2012 winter season, mainly due to the low amount of snow cover in that winter as a result of above-average temperatures.
+This is supported by the soil moisture anomaly (Figure~\ref{fig:anomalies_0}).
+(\textbf{I have a MODIS snow cover anomaly plot to show this, but I guess this would be overload?})}
 \label{fig:anomalies_vi}

### 2019-05-02 analysis.py

@@ -113,7 +113,12 @@ for key in h5.keys():
             df[key] = h5[key][:]
 print("Done")
 
+df['albedo_P'] = np.pi * df['meanrad1p'] / (np.cos(np.deg2rad(df['SZA'])) * 7.15e-6)
+df['albedo_S'] = np.pi * df['meanrad1s'] / (np.cos(np.deg2rad(df['SZA'])) * 7.15e-6)
 
+for pol in ['P', 'S']:
+    for win in ['755', '772']:
+        df[f'retr_albedo_{win}{pol}'] = df[f'r_svsv_cont_001_001_{win}_{pol}'] * df[f'albedo_{pol}']
 
 vi_fraction = pd.Series(index=np.arange(2010, 2017))
 planted_total = pd.Series(index=np.arange(2010, 2017))
@@ -392,7 +397,12 @@ def ts_overview(plot_df, sif_list, aux_list,
         else:
             aux_label = aux_labels[i]
 
-        ax.plot(plot_df.loc[:, aux],
+        if ('GPP' in aux_label) or ('NPP' in aux_label):
+            aux_data = plot_df.loc[:, aux] * 1e-3
+            aux_lim = aux_lim * 1e-3
+        else:
+            aux_data = plot_df.loc[:, aux]
+        ax.plot(aux_data,
                 #color=aux_colors[i],
                 label=aux_label, zorder=5)
         '''
@@ -419,6 +429,7 @@ def ts_overview(plot_df, sif_list, aux_list,
         ax2.plot(sif_data.median(axis=1),
                  color=sifcolor, linestyle='dashed', lw=1.0,
                  zorder=5)
+        #ax2.set_ylabel("SIF Anomaly")
         ax2.set_yticklabels([])
         ax2.legend(ax_handles, ax_labels,
                    fontsize=7, loc='lower left', framealpha=1.0)
@@ -511,7 +522,8 @@ aux_list = [#'gome2_sif',
     ####
     #'myd13_ndvi',
     #####
-    'CASA_GEE', 'CASA_NEE', 'uoe-7.1b']
+    'CASA_GEE', 'CASA_NEE', 'uoe-7.1b',
+    'albedo_P', 'retr_albedo_755P', 'albedo_S', 'retr_albedo_755S']
 
[…]

### 2019-05-02 quicklook_agriculture.py

@@ -53,6 +53,18 @@ df_pp_wheat =  pd.read_csv('progress_wheat.csv', sep=',', thousands=',')
 df_production = pd.read_csv('corn_soy_production.csv', sep=',', thousands=',')
 df_yield = pd.read_csv('corn_soy_yield.csv', sep=',', thousands=',')
 
+df_planted_soy = df_pp_soy.iloc[np.where(df_pp_soy["Data Item"] == "SOYBEANS - PROGRESS, MEASURED IN PCT PLANTED")[0],:]
+df_planted_corn = df_pp_corn.iloc[np.where(df_pp_corn["Data Item"] == "CORN - PROGRESS, MEASURED IN PCT PLANTED")[0],:]
+
+
+for week in range(16, 21):
+    cov = []
+    for year, dfp in df_planted_soy.query(f"Period == 'WEEK #{week}'").groupby("Year"):
+        #print(year, dfp.Value.mean(), dfp.Value.std())
+        cov.append(dfp.Value.std() / dfp.Value.mean())
+    print(week, np.mean(cov))
+
+
 # Quality
 df_status_corn = pd.read_csv('quality_all_corn.csv', sep=',', thousands=',')
 

### 2019-05-02 sampling_bias.py

@@ -92,7 +92,7 @@ lc_sort_GOSAT = np.argsort(lc_un_GOSAT[1])[::-1]
 
 # Make a nice barplot with the results
 bar_width = 0.25
-plt.figure(figsize=(2.5, 3), dpi=300)
+plt.figure(figsize=(2.0, 3), dpi=300)
 
 plt.barh(np.arange(len(lc_percs_ALL)) - bar_width / 2,
          lc_percs_ALL[lc_sort_ALL],
@@ -166,8 +166,8 @@ df_diff.loc['2015-01-01'] = np.nan
 fig = plt.figure(figsize=(3, 2), dpi=300)
 
 for x in lc_sort_ALL[:3]:
-    (df_diff[f'gosat_{x}'] - df_diff[f'all_{x}']).plot(label=lc_labels[x])
-fig.legend(bbox_to_anchor=(1.65, 0.85), ncol=1, fontsize=7)
+    (df_diff[f'gosat_{x}'] - df_diff[f'all_{x}']).plot(label=lc_labels[x], lw=1.0)
+fig.legend(bbox_to_anchor=(0.75, 1.35), ncol=1, fontsize=7)
 #fig.subplots_adjust(right=1.25)
 fig.tight_layout()
 plt.ylabel("LC coverage difference [$\%$]")

### 2019-05-02 snow_cover.py

@@ -1,0 +1,58 @@
+from pyhdf.SD import SD, SDC
+import numpy as np
+from matplotlib import pyplot as plt
+import glob
+from bbox import *
+from datetime import datetime as dt
+
+flist = dict.fromkeys(range(2010, 2017))
+for key in flist.keys():
+    flist[key] = np.sort(glob.glob(f"/Users/petersomkuti/Downloads/MYD10CM.A{key}*.hdf"))
+
+# Find the limits for the arrays
+lat = np.linspace(90 - 0.025, -90 + 0.025, 3600)
+lon = np.linspace(-180 + 0.025, 180 - 0.025, 7200)
+
+idx_lon_min = np.argmin(np.abs(lon - lon_min))
+idx_lon_max = np.argmin(np.abs(lon - lon_max))
+idx_lat_min = np.argmin(np.abs(lat - lat_min))
+idx_lat_max = np.argmin(np.abs(lat - lat_max))
+
+sc_array = np.ma.zeros((12 * 7, idx_lat_min - idx_lat_max, idx_lon_max - idx_lon_min))
+
+cnt = 0
+for year in range(2010, 2017):
+    for month in range(12):
+        print(year, month+1)
+        file = SD(flist[year][month], SDC.READ)
+        sc = file.select('Snow_Cover_Monthly_CMG').get()
+        sc_array[cnt, :, :] = sc[idx_lat_max:idx_lat_min, idx_lon_min:idx_lon_max]
+        file.end()
+        cnt += 1
+
+sc_array[sc_array > 100] = np.ma.masked
+
+sc_climatology = sc_array[:12].copy()
+for month in range(12):
+    sc_climatology[month] = np.ma.median(sc_array[month::12], axis=0)
+
+sc_anomaly = sc_array.copy()
+cnt = 0
+for year in range(2010, 2017):
+    for month in range(12):
+        sc_anomaly[cnt] = sc_array[cnt] - sc_climatology[month]
+        cnt += 1
+
+sc_thres = 25
+sc_fraction = []
+times = []
+
+cnt = 0
+for year in range(2010, 2017):
+    for month in range(12):
+        sc_fraction.append((sc_array[cnt].data > sc_thres).sum() / (~(sc_array[cnt].mask)).sum())
+        cnt += 1
+        times.append(dt(year, month+1, 15))
+
+
+plt.plot(times, sc_fraction); plt.show()
